\quad{}
\item \textbf{{[}ALVL/9597/2013/P1/Q2{]} }

A company keeps data about its employees. The employee surname and
employee ID are recorded. 

All employee IDs are unique and have the format C999 where C is any
uppercase letter and 9 is a digit.

A program is to be produced to search by either:
\begin{itemize}
\item The surname, which then reports the matching employee ID
\item The employee ID, which then reports the matching surname
\end{itemize}
The programmer stores the data a two 1-dimensional arrays and produces
the following search algorithm to search a string array and output
the matching value from the second array.

\noindent %
\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{INPUT SearchItem }

\texttt{FOR Index \textleftarrow{} 1 TO UpperBound }

\texttt{\qquad{}IF SearchItem = Array1{[}Index{]} }

\texttt{\qquad{}\qquad{}THEN OUTPUT Array2{[}Index{]} }

\texttt{\qquad{}ENDIF }

\texttt{ENDFOR}%
\end{minipage}

This search algorithm is inefficient.

The programmer uses the following design to produce the program code:
\begin{itemize}
\item code to search by surname 
\item The search algorithm has \texttt{Surname} as \texttt{Array1} and \texttt{EmployeeID}
as \texttt{Array2} followed by code to search by employee ID 
\item The search algorithm has \texttt{EmployeeID} as \texttt{Array1} and
\texttt{Surname} as \texttt{Array2}
\end{itemize}
This design would produce repetition of code.

\subsubsection*{Task 2.1}

Write program code which performs each of the searches:
\begin{itemize}
\item Search by surname 
\item Search by employee ID
\end{itemize}
Your code should address the issues of inefficiency and repetition
of code described in the scenario above. 

Use the sample array data available from the text file \texttt{EMPLOYEEDATA.txt}
and paste this into your program code.

\subsubsection*{Evidence 5}

Your program code.\hfill{} {[}11{]}

\subsubsection*{Task 2.2}

Devise a set of four test cases with the data to be used.

\subsubsection*{Evidence 6}

A screenshot for each test case you considered. Annotate the screenshot
explaining the purpose of each test. \hfill{}{[}4{]}