\item \textbf{{[}HCI/PRELIM/9597/2014/P2/Q1{]} }

Hwa Chong has partnered with Q\&M to set up a dental clinic in the
Campus. The clinic will have a few dentists to serve the student population.
The clinic will also have an on-line system for students to make appointment
with dentist. You are task to design the on-line system to handle
all student appointments. 
\begin{enumerate}
\item Draw an entity-relationship diagram for the appointment system. \hfill{}{[}7{]}
\item Convert the entity-relationship diagram into a relational database
schema. You may use shorthand notation to put across your answers.
Be certain to indicate the key fields. Your solution should include
a brief description for each table. \hfill{}{[}9{]}
\item Ensuring data integrity and security is an important issue in data
design. Explain why they are important for HC Dental system. \hfill{}{[}2{]}
\item The school plans to extent the dental service to other users after
the first year. Modify the entity relationship diagram to cater to
the teachers and staff too. \hfill{}{[}3{]}

Besides the data design, the user interface is an important factor
in determining the success of the HC dental system. The graphical
user interface for students to make an appointment using their desktops/laptops
must be intuitive and usable. 
\item Describe 3 design principles that will guide you in designing your
interfaces. Give specific examples on how you will incorporate it
into your user interface design for the HC dental system. \hfill{}{[}6{]}
\item Design the user-interfaces for the following features 
\begin{enumerate}
\item On-line appointment booking \hfill{}{[}3{]}
\item Updating of students particulars \hfill{}{[}3{]}
\end{enumerate}
\item Part of the future enhancement of the system is to allow a multimodal
interaction between the user and the system. A multimodal human-computer
interaction usually involves the 5 human senses and enables a more
free and natural communication. Suggest 2 realistic possibilities
for such an enhancement. Your suggestions should include a brief description
of how it works in this context.\hfill{}{[}4{]}

HC Dental system will reside in the school server and will allow access
beyond the school intranet. Mr Huang, the network administrator has
allocated an IP address 192.168.123.132 with a subnet mask 255.255.0.0
to access this system. 
\item Explain the following terms: 
\begin{enumerate}
\item IP address \hfill{}{[}1{]}
\item Subnet mask \hfill{}{[}1{]}
\end{enumerate}
\item Based on the information given, what is the network address? Show
the workings. \hfill{}{[}2{]}

The management team is concern with the accuracy of data transmitted/received
outside the school network. To ensure the team that they have looked
into this area, the development team highlighted that they have use
parity checks and checksums in detecting errors 
\item Explain parity checks and give an example to illustrate how it works.
\hfill{}{[}2{]}

The network administrator highlighted that there are proxy and firewalls
settings for devices accessing the school network. 
\item What is the purpose of a proxy server in the Network? \hfill{}{[}2{]}
\end{enumerate}