\item \textbf{{[}HCI/PRELIM/9597/2014/P1/Q4{]} }

Many programming languages use a variety of brackets eg \texttt{()},
\texttt{\{\}} and \texttt{{[}{]}} in their program statement constructs.
Brackets can be nested e.g. (()) and \{{[}{]}\}. A well-formed construct
must contain a matched set of optionally nested brackets e.g.\texttt{ (())},
\texttt{\{{[}{]}\}} and \texttt{()\{\}{[}{]}} are well-formed whereas\texttt{
(()},\texttt{ \{{]} }and\texttt{ )( }are not. 

An efficient way to check if a program construct is well-formed is
to use a stack to scan the brackets once from left to right as follows: 

Start from an empty stack. Whenever we encounter an open bracket,
push it into the stack. Whenever we encounter a close bracket, we
check if it is of the same type with the item at the top of the stack.
Once we have a match, we pop the topmost bracket from the stack. Only
when we managed to read the last bracket and find that the stack is
empty, then we know that the brackets are properly nested, and the
program construct is well-formed. 

The stack ADT contains character data and a top pointer, and has the
following operations: 
\begin{itemize}
\item \texttt{Create()} : initializes a new stack 
\item \texttt{Push(item)} : add item to top of stack 
\item \texttt{Pop()} : remove item from top of stack 
\item \texttt{Peep()} : inspect the topmost item of stack 
\item \texttt{isEmpty()} : check if stack is empty 
\end{itemize}

\subsection*{Task 4.1 }

Using object-oriented programming techniques, implement the stack
ADT using the class name \texttt{Stack}. 

\subsection*{Evidence 16: }

Your \texttt{Stack} class program code. \hfill{}{[}8{]}

\subsection*{Task 4.2 }

Write a function \texttt{CheckNested(construct)} which accepts a string
program construct of nested brackets and returns a Boolean result
indicating if construct is well-formed. 

\subsection*{Evidence 17: }

Your \texttt{CheckNested} function code. \hfill{}{[}10{]}

\subsection*{Task 4.3}

Test your \texttt{CheckNested} function using the data file provided
in \texttt{DATA.txt}. If a construct is not well-formed, append it
to a text file \texttt{ERRORS.txt}. 

\subsection*{Evidence 18: }

Screenshot of \texttt{ERRORS.txt}. \hfill{}{[}1{]}

\subsection*{Task 4.4}

Write a function \texttt{CheckWellformed(construct)} which contains
a modified and enhanced version of \texttt{CheckNested(construct)}.
When a first mismatch of bracket occurs, output the diagnostic message
\texttt{\textquotedbl Expecting '?'\textquotedbl}, where ? is the
type of bracket expected. For example, for the construct \texttt{())},
output the diagnostic message \texttt{\textquotedbl Expecting '('\textquotedbl}. 

\subsection*{Evidence 19: }

Your \texttt{CheckWellformed} function code. \hfill{}{[}10{]}

\subsection*{Task 4.5}

Test your \texttt{CheckWellformed} function using \texttt{ERRORS.txt}.
Display the diagnostic messages to screen.

\subsection*{Evidence 20: }

Screenshot of diagnostic messages on screen. \hfill{}{[}1{]}