\item \textbf{{[}PJC/PRELIM/9597/2014/P1/Q2{]} }

A pseudocode algorithm for a binary search on an array \texttt{CITY}
is shown below. This array stores records of city, and its country
and population. Array is sorted by name of city. It has an initial
subscript 1 and final subscript \texttt{MAX}. The algorithm can be
improved to make it clearer and more efficient. 

\noindent %
\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{Set element\_found to false }

\texttt{Set low\_element to 1 }

\texttt{Set high\_element to MAX }

\texttt{\textbf{DOWHILE}}\texttt{ (NOT element\_found)}

\texttt{\qquad{}index = (low\_element + high\_element)/2 }

\texttt{\qquad{}}\texttt{\textbf{IF}}\texttt{ CITY(index) = input\_value
}\texttt{\textbf{THEN}}\texttt{ }

\texttt{\qquad{}\qquad{}Set element\_found to true }

\texttt{\qquad{}}\texttt{\textbf{ELSE}}\texttt{ }

\texttt{\qquad{}\qquad{}}\texttt{\textbf{IF}}\texttt{ input\_value
<= CITY(index) }\texttt{\textbf{THEN}}\texttt{ }

\texttt{\qquad{}\qquad{}\qquad{}high\_element = index \textendash{}
1 }

\texttt{\qquad{}\qquad{}}\texttt{\textbf{ELSE}}\texttt{ }

\texttt{\qquad{}\qquad{}\qquad{}low\_element = index + 1 }

\texttt{\qquad{}\qquad{}}\texttt{\textbf{ENDIF}}

\texttt{\qquad{}}\texttt{\textbf{ENDIF}}\texttt{ }

\texttt{\textbf{ENDDO}}

\texttt{\textbf{IF}}\texttt{ element\_found = true }\texttt{\textbf{THEN}}\texttt{ }

\texttt{\qquad{}Print index}

\texttt{\textbf{ELSE}}\texttt{ }

\texttt{\qquad{}Print \textquotedbl sorry\textquotedbl{} }

\texttt{ENDIF }%
\end{minipage}

\subsection*{Task 2.1 }

Write program code for this algorithm and improve on clarity and efficiency.
Include the sample array data available by reading from the file \texttt{CITY.csv}.
If a city is found after searching, display the full record of the
city, which includes country and population. 

\subsection*{Evidence 5: }

Your program code. \hfill{} {[}6{]}

\subsection*{Evidence 6: }

Produce a screenshot of running your program code, by searching for
\texttt{\textbf{Istanbul}} and \texttt{\textbf{Aberdeen}}. \hfill{}
{[}2{]}

\subsection*{Task 2.2 }

Write the binary search algorithm as a recursive function. Using comment
lines, explain on your choice of parameters passed into the recursive
function and return value, if any. 

\subsection*{Evidence 7: }

Your program code. \hfill{} {[}7{]}