\item \textbf{{[}PJC/PRELIM/9597/2014/P2/Q5{]} }

Pioneer Book Store sells books online and charges for delivery. Its
delivery charges for orders less than \$200 are as follows: 
\begin{itemize}
\item If the number of items is 3 or less, delivery by next day will be
charged at \$30, while standard delivery will be charged at \$2 per
item. 
\item If the number of items is 4 or more, delivery by next day will be
charged at \$5 per item, while standard delivery is free.
\end{itemize}
For orders more than \$200, standard delivery is free for any number
of items, while delivery by next day will be charged at \$5 per item.
\begin{enumerate}
\item Draw a decision table showing clearly the different conditions and
actions, removing the redundancies.\hfill{} {[}6{]}
\end{enumerate}
Customers can view a catalogue of books and order from its website.
Payment is made by the customer forwarding their credit card details,
which are processed immediately. Details of the orders are matched
against the stock file to check for availability of items before packing
lists are produced and sent to the packing department. 
\begin{enumerate}
\item[(b)]  Draw a data flow diagram to explain the flow of data through this
system.\hfill{} {[}6{]}
\end{enumerate}
New customers have to register with the online book store from its
website before they can make any orders. 
\begin{enumerate}
\item[(c)]  Design a suitable user interface for a new customer to register
with the online book store, showing its possible contents in terms
of options presented to the user, justifying your design. \hfill{}{[}4{]}
\end{enumerate}