\item \textbf{{[}DHS/PRELIM/9597/2014/P2/Q1{]} }

The Pioneer Generation Joint Committee (PGJC) is a diverse taskforce
set up to manage and promote information about the Pioneer Generation
Package (PGP) to honour and thank pioneers for their hard work and
dedication to make Singapore what it is today. The PGP will benefit
about 450,000 Singaporeans. 

Beyond the conventional means of raising awareness of PGP via mainstream
media (newspapers and television broadcast), PGJC also desires to
enhance its outreach using the Internet, new media (e.g. social networks)
and mobile applications. 
\begin{enumerate}
\item Give two advantages of using the latter modes of outreach compared
to traditional mass media. \hfill{}{[}2{]}
\item A significant challenge of using non-conventional outreach methods
is that while the Internet and mobile devices are becoming increasingly
ubiquitous, many user interfaces are often not well suited to the
elderly's specific needs. 

Design and justify an appropriate user interface for a pioneer to
enter information to file for hospitalisation claim on an insurance
company's website using a desktop or laptop computer. The information
required are: NRIC, hospital name, from and to dates of hospitalisation,
invoice number, invoice amount and brief description of reason for
hospitalisation. \hfill{}{[}4{]}
\item Give two factors developers would need to consider to adapt the user
interface for a mobile device such as a smartphone. \hfill{}{[}2{]}
\item The development of the PGP mobile application will involve the following
phases: 
\noindent \begin{center}
\begin{tabular}{|c|l|c|c|}
\hline 
Phase & Description & Duration(mandays) & Preceding Phase\tabularnewline
\hline 
\hline 
A & Adapt contents for smaller form factors & 8 & -\tabularnewline
\hline 
B & Prepare development environment & 2 & A\tabularnewline
\hline 
C & Purchase developer license (include approval time)  & 2 & B\tabularnewline
\hline 
D & Develop and test for Android & 4 & C\tabularnewline
\hline 
E & Develop and test for iOS & 3 & C\tabularnewline
\hline 
F & Publish to Google Play & 1 & D\tabularnewline
\hline 
G & Publish to App Store & 5 & E\tabularnewline
\hline 
H & Promotion and marketing & 3 & F, G\tabularnewline
\hline 
\end{tabular}
\par\end{center}
\begin{enumerate}
\item Construct a PERT chart for this project.\hfill{} {[}3{]}
\item State the critical path and the total time required for the project.\hfill{}
{[}2{]}
\item There is also a need to maintain documentation for the project. Why
is documentation important? \hfill{}{[}2{]}
\item Construct a Gantt chart to include and justify a documentation phase
of a reasonable duration.\hfill{} {[}3{]}
\end{enumerate}
\end{enumerate}
The following screenshot shows the user interface where a pioneer
can verify his/her eligibility. 
\noindent \begin{center}
<INSERT\_IMAGE\_HERE>
\par\end{center}
\begin{enumerate}
\item[(e)]  The code below the NRIC field shows a randomly generated string. 
\begin{enumerate}
\item Explain the purpose of this code. \hfill{}{[}1{]}
\item Outline an algorithm to generate another random string when the refresh
button is clicked.\hfill{} {[}3{]}
\end{enumerate}
\item[(f)]  Using examples from the above user interface, explain the following
concepts: 
\begin{enumerate}
\item (i) validation and verification \hfill{}{[}4{]}
\item (ii) client-side and server-side scripting \hfill{}{[}4{]}
\end{enumerate}
\item[(g)]  Information is transmitted to the server using the https protocol.
\begin{enumerate}
\item Explain the significance of this protocol.\hfill{} {[}2{]}
\item Describe how information is typically transmitted between a client
and a server. \hfill{}{[}3{]}
\end{enumerate}
\end{enumerate}