\item \textbf{{[}ALVL/9597/2015/P1/Q1{]} }

The file \texttt{ADMISSIONS-DATA.TXT} contains the daily total admissions
to a theme park over a period of 50 days. 

The task is to read the numbers from the file and display a sorted
list. 

You will program two different sort algorithms: 
\begin{enumerate}
\item A bubble sort. 
\item Either a quick sort or an insertion sort but not both. 
\end{enumerate}
Task 1.1

Write code for a procedure to display a menu with the following options: 
\begin{center}
\noindent\ovalbox{\begin{minipage}[t]{1\columnwidth - 2\fboxsep - 0.8pt}%
\begin{enumerate}
\item[1]  Read file data
\item[2] Bubble sort
\item[3] Quick sort/ Insertion sort
\item[4] End Task
\end{enumerate}
%
\end{minipage}}
\par\end{center}

\subsubsection*{Task 1.2}

Write the program code for a procedure to implement menu option 1.

\subsubsection*{Evidence 1}
\begin{itemize}
\item The program code for the menu. 
\item Program code for menu option 1. \hfill{}{[}5{]} 
\end{itemize}
Options 2 and 3 will sort and display the sorted data. The algorithm
for a bubble sort is given in file \texttt{BUBBLE.TXT}. 

Write program code as a procedure to implement the bubble sort. 

\subsubsection*{Evidence 2}
\begin{itemize}
\item The bubble sort code procedure. \hfill{}{[}1{]}
\end{itemize}
Write program code as a procedure to implement the quick sort or the
insertion sort. 

\subsubsection*{Evidence 3}
\begin{itemize}
\item Indicate the sort method used.
\item The program for the sort method used. \hfill{}{[}4{]}
\end{itemize}


\subsubsection*{Task 1.3}

Additional code is to be written for each sort procedure. The sort
methods will count and display the number of comparisons made in completing
the sort process. This will provide an indicator of the efficiency
of each algorithm.

Write the additional code to count and display the number of comparisons
made for each sort method.

\subsubsection*{Evidence 4}
\begin{itemize}
\item The output from menu option 2. \hfill{} {[}2{]}
\end{itemize}

\subsubsection*{Evidence 5}
\begin{itemize}
\item The output from menu option 3. \hfill{} {[}2{]}
\end{itemize}