\item \textbf{{[}DHS/PRELIM/9597/2015/P2/Q1{]} }

A young family decides to purchase a new car. The following precedence
table shows the constituent activities with their preceding activities
and durations. 
\noindent \begin{center}
\begin{tabular}{|c|c|c|c|}
\hline 
Activity & Description & Preceding Activity & Duration (days) \tabularnewline
\hline 
A & Decide feasibility of purchase & - & 3\tabularnewline
\hline 
B & Find buyer for existing car & A & 14\tabularnewline
\hline 
C & Decide on possible models & A & 1\tabularnewline
\hline 
D & Investigate decided models & C & 2\tabularnewline
\hline 
E & Discuss with knowledgeable friends & C & 1\tabularnewline
\hline 
F & Get information from dealers & C & 2\tabularnewline
\hline 
G & Put together all information & D, E, F & 1\tabularnewline
\hline 
H & Shortlist three options & G & 1\tabularnewline
\hline 
I & Test drive shortlisted options & H & 3\tabularnewline
\hline 
J & Get finance information & H & 2\tabularnewline
\hline 
K & Confirm car model & I, J & 2\tabularnewline
\hline 
L & Compare dealers and choose one & K & 2\tabularnewline
\hline 
M & Decide on colour & L & 4\tabularnewline
\hline 
N & Test drive chosen model & L & 1\tabularnewline
\hline 
O & Buy new car & B, M, N & 3\tabularnewline
\hline 
\end{tabular}
\par\end{center}
\begin{enumerate}
\item Discuss how the family can conduct a feasibility study for the purchase.\hfill{}
{[}3{]}
\item Construct a PERT chart for this project. \hfill{}{[}4{]}
\item State the critical path and the total time required for the project.
\hfill{}{[}2{]}
\item Name a floating task and state its role in the project.\hfill{} {[}2{]}
\item Explain the significance of dummy activities in this project.\hfill{}
{[}3{]}
\item Construct the corresponding Gantt chart for the project. \hfill{}{[}3{]}
\item Why should one derive the PERT chart before the Gantt chart?\hfill{}{[}2{]}
\item How does a Gantt chart help in the project?\hfill{} {[}3{]}
\item Suggest two reasons why activity M requires 4 days. What can be done
to speed this up?\hfill{} {[}3{]}
\item In activity E, the family decides to use a cross-platform mobile messaging
app which allows users to exchange messages without having to pay
for SMS. Communication with its network of knowledgeable friends requires
the use of TCP/IP sockets. What is a TCP/IP socket and how does it
help in network communication? \hfill{}{[}3{]}
\item A number of activities require the use of an Internet search engine.
Explain how an Internet search engine works and how cloud computing
is used in implementing an Internet search engine. \hfill{}{[}8{]}
\item After the car purchase, the family decides to share their experience
using either a personal blog post or a social network post to benefit
other potential car buyers. Compare the relative pros and cons of
using these approaches. \hfill{}{[}4{]}
\end{enumerate}