\item \textbf{{[}DHS/PRELIM/9597/2015/P1/Q1{]} }

The coming General Election will see 28481 voters in the MacPherson
Single Member Constituency (SMC) voting for their Member of Parliament
(MP). The data file \texttt{ELECTION.txt} contains the simulated voting
results, with A, B, C and V representing votes for the political parties
National Solidarity Party, People Action Party and Workers' Party,
as well as void votes respectively. 

\subsection*{Task 1.1}

Determine the winner and the voting statistics (correct to 1 decimal
place) for this SMC. Your output should look like the following: 

Sample output: 

\noindent %
\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{Results for the Electoral Division of MacPherson }

\texttt{PAP 58.7\%}

\texttt{WP 37.5\%}

\texttt{NSP 2.6\% }

\texttt{Void 1.2\%}

\texttt{Winner is PAP }%
\end{minipage}

\subsection*{Evidence 1 }

Program code. \hfill{}{[}7{]}

\subsection*{Evidence 2}

Screenshot.\hfill{} {[}1{]}

\subsection*{Task 1.2}

In the event of a tie, the parties tied will enter into a revoting
exercise. For example, if there is a tie between PAP and WP, return
the message \textquotedbl\texttt{Revote between PAP and WP}\textquotedbl . 

Write program code to generate a text file \texttt{TIE.txt} with approximately
3\% void votes, 7\% votes for NSP and a tie between PAP and WP. Test
your program with your generated \texttt{TIE.txt}. 

\subsection*{Evidence 3 }

Program code.\hfill{} {[}6{]}

\subsection*{Evidence 4 }

Screenshot. \hfill{}{[}1{]}