\item \textbf{{[}DHS/PRELIM/9597/2015/P2/Q4{]} }

A durian specialty business sells its different breeds of durians
via two modes currently: 
\begin{itemize}
\item phone order via calling in to its sales hotline
\item web order via making an online order on its website 
\end{itemize}
For phone order, a sales agent will record the order details (breed,
quantity, customer name and phone number). Payment terms will be cash
on collection only. For web order, the customer will register for
an account using his/her email address and select the breed and quantity,
and enter his/her phone number. Payment terms will be either cash
on collection or by entering credit card details upon checkout.
\begin{enumerate}
\item Using suitable examples from this context, explain the concepts of
\begin{enumerate}
\item validation \hfill{}{[}2{]}
\item verification \hfill{}{[}2{]}
\end{enumerate}
\item Draw a UML class diagram to show the relationship between the different
types of orders.\hfill{}{[}4{]}
\item Using suitable examples, explain the concepts of 
\begin{enumerate}
\item encapsulation \hfill{}{[}2{]}
\item inheritance\hfill{} {[}2{]}
\item polymorphism \hfill{}{[}2{]}
\end{enumerate}
\item To cater to an aging population and elderly who face difficulty using
smartphones, it is proposed that an SMS application be developed to
allow elderly to order durians using SMS. Design and justify a suitable
user interface and workflow. Assume that the SMS sales number is 88387426
(88DURIAN).\hfill{} {[}3{]}
\end{enumerate}