\item \textbf{{[}ALVL/9597/2015/P1/Q2{]} }

The pseudocode procedure below is given a denary number. The procedure
then outputs the binary equivalent of the denary number.

\noindent %
\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{PROCEDURE Converter(DenaryNumber : INTEGER) }

\texttt{\qquad{}IF DenaryNumber = 0 OR DenaryNumber = 1 }

\texttt{\qquad{}\qquad{}THEN }

\texttt{\qquad{}\qquad{}\qquad{}OUTPUT DenaryNumber }

\texttt{\qquad{}\qquad{}ELSE }

\texttt{\qquad{}\qquad{}\qquad{}OUTPUT DenaryNumber MOD 2 }

\texttt{\qquad{}\qquad{}\qquad{}Converter(DenaryNumber DIV 2) }

\texttt{\qquad{}ENDIF }

\texttt{ENDPROCEDURE}%
\end{minipage}

\subsubsection*{Task 2.1}

Write program code to implement the given procedure. 

Execute the procedure using 56 as the parameter. 

\subsubsection*{Evidence 6}
\begin{itemize}
\item Program code. 
\item Screenshot showing the output. \hfill{}{[}6{]}
\end{itemize}

\subsubsection*{Task 2.2}

There is an error with the given algorithm. 

Describe the error and the effect it created on the output in Evidence
6. 

\subsubsection*{Evidence 7}
\begin{itemize}
\item Statement(s) to answer Task 2.2. \hfill{}{[}1{]}
\end{itemize}

\subsubsection*{Task 2.3}

Make changes to the procedure Converter which will correct the error. 

Draw up a list of test cases for the testing of the amended code.
by completing a table with the following headings: 
\begin{center}
\begin{tabular}{|l|l|l|}
\hline 
\texttt{DenaryNumber} & Purpose of the test & Expected output\tabularnewline
\hline 
 &  & \tabularnewline
\hline 
$\vdots$ & $\vdots$ & $\vdots$\tabularnewline
\hline 
 &  & \tabularnewline
\hline 
\end{tabular}
\par\end{center}

\subsubsection*{Evidence 8}
\begin{itemize}
\item The amended PROCEDURE Converter program code.
\item The completed table. 
\item Screenshots for two of the tests. \hfill{}{[}11{]}
\end{itemize}