\item \textbf{{[}HCI/PRELIM/9597/2016/P2/Q2{]} }

The owner of HC Book Café wishes to converts his book café into a
self-service book club café for members only. All access to food or
books is via a \textquotedblleft vending machine\textquotedblright{}
concept using the member\textquoteright s card. 

There is a stock of 2000 different book titles and multiple copies
of popular titles. Books may be hired by members. Different rates
are charged for different books. Members are allowed to hire no more
than 5 items at anytime. 

Members can enjoy a light snack while viewing their favourite book.
If the book is returned the same day via the book drop, hire charges
are not incurred. All food and hire charges incurred for the month
is billed to the member every 12th of the following month. Cash transaction
is not available. 

The shop owner wishes to computerize the system to handle the various
transactions and stock control. The system should also perform the
following functions: 
\begin{itemize}
\item Hold up-to-date details of members and stock
\item Allow enquiry to determine the whereabouts, and dates of return, of
particular books 
\item Produce an itemized bill for each customer at end of each month.
\end{itemize}
\begin{enumerate}
\item The system analyst of a software house was to design the computerized
system. What documentation should the system analyst produce and state
5 necessary contents of the documentation? Who would use it and state
2 reasons for use.\hfill{} {[}8{]}
\item List the files, giving details of the fields which it may contain,
that would be required for this system, and draw the data flow diagram
of the computerized system. \hfill{} {[}12{]}
\item HC Book Café offers a member loyalty program that offers a range of
discounts. For members in the loyalty program between 3 to 5 years,
they will receive a 5\% discount. For more than 5 years, the member
will receive a 10\% discount. However, whether a member is in the
loyalty program or not, if the cumulative value of his transactions
for this calendar year exceed \$1000, he will receive a 15\% discount.
However, note that aggregation of discounts is not allowed. 
\begin{enumerate}
\item Create a decision table that shows all possible outcomes for the above
loyalty program. 
\item Draw the decision table after redundancies have been removed. \hfill{}
{[}5{]}
\end{enumerate}
\end{enumerate}