\item \textbf{{[}PJC/PRELIM/9597/2016/P1/Q3{]} }

Tic-tac-toe is a game in which two players take turns marking X and
O in the spaces in a $3\times3$ grid. The player who succeeds in
placing three of their marks in a horizontal, vertical, or diagonal
row wins the game.

For example, player who marks \texttt{X} wins this game. 
\noindent \begin{center}
\begin{tabular}{|c|c|c|}
\hline 
\texttt{X} & \texttt{O} & \tabularnewline
\hline 
\texttt{X} & \texttt{X} & \texttt{X}\tabularnewline
\hline 
\texttt{O} &  & \texttt{O}\tabularnewline
\hline 
\end{tabular}
\par\end{center}

The task is to write program code for a tic-tac-toe game for two human
players. 

\subsection*{Task 3.1 }

Decide on the design to be used for:
\begin{itemize}
\item the data structure to represent the $3\times3$ grid, using the identifier
\texttt{board}
\item the contents of the marks (\texttt{X}, \texttt{O} and blank) in the
spaces
\item how user input (\texttt{X} or \texttt{O}) in the spaces 
\end{itemize}

\subsection*{Evidence 10:}

Your program design. Include program code for board. \hfill{} {[}4{]}

\subsection*{Task 3.2 }

Write a function \texttt{displayBoard} that will display the game
\texttt{board} clearly to the players. You should use the board as
a parameter in \texttt{displayBoard}. 

Write another function \texttt{displayInstructions} to inform players
on how to input \texttt{X} and \texttt{O} in the spaces on the game
board. 

\subsection*{Evidence 11: }

Your functions \texttt{displayBoard} and \texttt{displayInstructions}.
\hfill{}{[}4{]}

\subsection*{Task 3.3 }

Write a function \texttt{getPlayerMove} to get players to make their
move (by marking \texttt{X} or \texttt{O}) on the board. You should
include validation on user input and check that the space is not already
occupied. Use \texttt{board} as a parameter. You may include any other
suitable parameters. 

\subsubsection*{Evidence 12: }

Your function \texttt{getPlayerMove}. \hfill{}{[}5{]}

\subsection*{Task 3.4 }

Write a function \texttt{checkWin} that checks all the conditions
for winning a game and returns \texttt{True} if a player has won the
game, otherwise return \texttt{False}. Use \texttt{board} as a parameter.
You may include any other suitable parameters. 

\subsection*{Evidence 13:}

Your function \texttt{checkWin}. \hfill{}{[}5{]}

\subsection*{Task 3.5}

Write a \texttt{main} function that makes use of the identifiers and
functions from task 3.1 to task 3.4 and allows two human players to
play a game of tic-tac-toe.

The \texttt{main} function should include the following: 
\begin{itemize}
\item give instructions to players on how to input \texttt{X} or \texttt{O} 
\item ask whether player 1 or player 2 starts first move 
\item ensure players 1 and 2 take turns to make their move 
\item display the game board after every move made by a player
\item check for winner
\item display message on which player has won the game or whether the game
ends in a draw
\end{itemize}

\subsection*{Evidence 14: }

Your \texttt{main} function. \hfill{} {[}8{]}

\subsection*{Evidence 15: }

Run your \texttt{main} function and produce screenshots of \textbf{three}
games where player 1 wins one game, player 2 wins another game, and
a drawn game. \hfill{}{[}3{]}