\item \textbf{{[}ALVL/9597/2016/P2/Q6{]} }

A real-estate management company owns a number of residential and
business units. When the company first acquires a unit, it often requires
renovation work. The company records the renovation cost.

A residential unit will be a house or an individual flat within a
building. A business unit will be either an office building, a storage
unit or a factory.

A residential unit is either advertised for sale, with the company
looking to make a profit, or retained for rental. If the unit is sold,
the sale price is recorded. If the unit is retained, the monthly rental
charged, the start date and length of the rental (in months) are recorded.

A business unit has a long term lease, which is usually 10 years or
longer. The company records the nature of the business. it does not
offer any of its business units for sale. 

Other data recorded for a unit include: purchase price, purchase date,
number of rooms, floor space, whether or not a lift is present. The
company records whether the house has a garage and whether it has
a garden. 

A programmer will develop an application, using object-oriented programming
to store and process the company\textquoteright s data. 
\begin{enumerate}
\item Draw a class diagram, with base class \texttt{UNIT}, showing: 
\begin{itemize}
\item appropriate sub-class(es)
\item inheritance 
\item the properties required 
\item appropriate methods, including \textbf{one} pair of \textquoteleft get\textquoteright{}
and \textquoteleft set\textquoteleft{} methods for \textbf{one} of
the properties.\hfill{} {[}8{]}
\end{itemize}
\item The company has recently purchased a number of units that they want
to renovate as a \textquoteleft block of flats\textquoteright{} (a
number of self-contained flats in the same building). Once the renovation
is complete, the company may offer a block of flats for sale. Alternatively,
it may retain the unit and advertise each individual flat for rental. 

Explain how this would affect the design in \textbf{part (a)}. \hfill{}{[}3{]}
\item {}
\begin{enumerate}
\item Explain the meaning of the term encapsulation. \hfill{}{[}2{]}
\item Explain the meaning of the term polymorphism. \hfill{}{[}2{]}
\end{enumerate}
\end{enumerate}