\item \textbf{{[}HCI/PRELIM/9597/2017/P1/Q2{]} }

The files \texttt{CUPS-SOLD1.txt} and \texttt{CUPS-SOLD2.txt} contain
the daily total number of cups of coffee sold at a café over a period
of 50 days. The task is to read the daily sales from the file and
to allow a search for a specific sales figure. You will program two
different search algorithms: 
\begin{itemize}
\item Linear Search 
\item Binary Search 
\end{itemize}

\subsection*{Task 2.1 }

Write program code that repeatedly: 
\begin{itemize}
\item displays a menu with the following options:
\noindent \begin{center}
\begin{tabular}{|l|}
\hline 
1. Read File\tabularnewline
2. Linear Search\tabularnewline
3. Binary Search\tabularnewline
4. End\tabularnewline
\hline 
\end{tabular}
\par\end{center}
\item calls an appropriate procedure/function depending on the user\textquoteright s
option.
\end{itemize}

\subsection*{Evidence 6 }

Program code for Task 2.1. \hfill{}{[}3{]}

\subsection*{Task 2.2 }

Write the program code for a procedure to implement menu option 1. 

\subsection*{Evidence 7 }

Program code for menu option 1. \hfill{}{[}2{]}

Options 2 and 3 will perform a search for a specified sales figure
and display a message to indicate if it is found or not. 

\subsection*{Task 2.3}

Write program code as a function to implement the linear search for
menu option 2. The function will return 0 if the sales figure is found,
or -1 if it is not found. 

The program will: 
\begin{itemize}
\item Input a sales figure 
\item Use the function \texttt{LinearSearch} 
\item Report whether or not this sales figure was found.
\end{itemize}
Use \texttt{CUPS-SOLD1.txt} to test your program code. 

Run the program two times. Use the following inputs: \texttt{167}
and \texttt{405}. 

\subsection*{Evidence 8}
\begin{itemize}
\item Program code for menu option 2.
\item Screenshots showing the output from menu option 2. \hfill{}{[}5{]}
\end{itemize}

\subsection*{Task 2.4 }

Write program code as a function to implement the binary search for
menu option 3. The function will return \texttt{0} if the sales figure
is found, or \texttt{-1} if it is not found. 

\textbf{{*}Hint: Do not use any pre-defined sort function e.g. sort()
in your program code.}

The program will: 
\begin{itemize}
\item Input a sales figure
\item Use the function \texttt{BinarySearch} 
\item Report whether or not this sales figure was found.
\end{itemize}
Use \texttt{CUPS-SOLD1.txt} to test your program code. Run the program
two times. Use the following inputs: \texttt{366} and \texttt{123}. 

\subsection*{Evidence 9 }
\begin{itemize}
\item Program code for menu option 3. 
\item Screenshots showing the output from menu option 3. \hfill{}{[}10{]}
\end{itemize}

\subsection*{Task 2.5}

Amend your program code for the linear search function so that if
the specified sales figure exists, the number of day(s) with this
sales figure is also reported. 

Use the file \texttt{CUPS-SOLD2.txt} to test your program. 

\subsection*{Evidence 10 }

The amended program code for menu option 2. \hfill{}{[}3{]}

\subsection*{Task 2.6}

Study the contents of \texttt{CUPS-SOLD2.txt} and then devise a set
of three test cases with the sales figures to be used for testing
the amended code. Evidence 11 A screenshot for each test case you
considered. Annotate the screenshot explaining the purpose of each
test. \hfill{}{[}3{]}