\item \textbf{{[}HCI/PRELIM/9597/2017/P1/Q1{]} }

A web log,\texttt{ WEBLOG.txt}, keeps track of the date and time the
server is being accessed, and the client that accessed it. The client
is identified by either the host name or internet address. The format
of \texttt{WEBLOG.txt} is as follows: 
\noindent \begin{center}
\texttt{<host name>|<DD/MMM/YYYY:HH:MM:SS> }
\par\end{center}

or
\noindent \begin{center}
\texttt{<internet address>|<DD/MMM/YYYY:HH:MM:SS> }
\par\end{center}

Below is a sample of \texttt{WEBLOG.txt}: 

\noindent\fbox{\begin{minipage}[t]{1\columnwidth - 2\fboxsep - 2\fboxrule}%
\texttt{199.72.81.55|01/Jul/1995:00:00:01 }

\texttt{unicomp6.unicomp.net|01/Jul/1995:00:00:06 }

\texttt{199.120.110.21|01/Jul/1995:00:00:09 }

\texttt{burger.letters.com|01/Jul/1995:00:00:11} %
\end{minipage}}

The client address (host name or internet address) can appear multiple
times, depending on how many times it accessed the server. Similarly,
the date it accessed the server can be duplicated too because it can
access the server many times in a day. 

A summary report, SUMMARY.txt, is to be generated to list the \textbf{unique}
clients (hosts name/internet address) and the corresponding list of
\textbf{unique} dates that it has accessed the server, from the web
log, \texttt{WEBLOG.txt}. 

Below is a sample of \texttt{SUMMARY.txt}: 

\noindent\fbox{\begin{minipage}[t]{1\columnwidth - 2\fboxsep - 2\fboxrule}%
\texttt{199.72.81.55 01/Jul/1995,03/Jul/1995,04/Jul/1995 }

\texttt{Buger.letters.com 01/Jul/1995,05/Jul/1995}

\texttt{Computing.com 01/Jul/1995,02/Jul/1995,03/Jul/1995}%
\end{minipage}}

\subsection*{Task 1.1}

Write a procedure \texttt{ReadLog()} to read \texttt{WEBLOG.txt},
using a suitable data structure(s), and prepare the log information
to create \texttt{SUMMARY.txt}.

\subsection*{Evidence 1 }

Your \texttt{ReadLog()} procedure code. \hfill{}{[}4{]}

\subsection*{Task 1.2 }

Write a procedure \texttt{ProcessLog()} to generate \texttt{SUMMARY.txt}. 

\subsection*{Evidence 2}

Your \texttt{ProcessLog()} procedure code.\hfill{} {[}4{]}

\subsection*{Evidence 3 }

Screenshot of \texttt{SUMMARY.txt} after running the program. \hfill{}{[}1{]}

\subsection*{Task 1.3 }

Add code to your Task 1.2 program to output to screen the highest
number of days the server was accessed by any client, and the corresponding
client(s). Below is a sample of screen output:

\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{Highest frequency (days): 3 }

\texttt{Accessed by: }

\texttt{199.72.81.55}

\texttt{Computing.com}%
\end{minipage}

\subsection*{Evidence 4}

Your program code for Task 1.3.\hfill{} {[}4{]}

\subsection*{Evidence 5}

Screenshot of the program output. \hfill{}{[}1{]}