\item \textbf{{[}ALVL/9597/2017/P2/Q1{]} }

The principal of a college decides to improve security access. Currently,
the staff use keys to enter classrooms and laboratories. One of the
principal\textquoteright s suggested improvements is to replace the
existing locks and keys with a swipe card system. The principal plans
to purchase swipe card readers for every room, and staff will be issued
with their own swipe card. if a valid card is swiped through a particular
reader, the corresponding door will be unlocked.

Software for controlling the system is required to: 
\begin{itemize}
\item define the rooms that can be entered by each card. The office staff
will make any changes. 
\item produce a pop-up screen on the office staff's computer if an unauthorised
card is used to attempt an entry into a room. 
\item produce reports. Some of the reports will be confidential and can
only be viewed by the principal. 
\end{itemize}
A local software company is selected to produce the software. The
company assigns a development team to the project. 
\begin{enumerate}
\item A systems analyst from the team makes an initial visit to the college. 

State two groups of staff that the systems analyst would need to interview.
Justify your answer. \hfill{}{[}4{]}
\item As a result of the analysis carried out. a diagram is used to show
entities and data flow. Draw a suitable diagram. \hfill{}{[}6{]}
\item The next stage of system development is software design.
\begin{enumerate}
\item Describe the checks that the team needs to make at the end of this
stage. \hfill{}{[}2{]}
\item Describe two methods that could be used to check this design. For
each method, identify the members of the development team involved
other than the systems analyst. {[}6{]}
\end{enumerate}
\item The swipe card system will need to be fully tested. The company carries
out white box and black box testing. 

Explain \textbf{three} differences between black box and white box
testing. \hfill{}{[}6{]}
\item User documentation will be produced during the development process. 

Describe \textbf{three} sections that should be included in the user
guide for this system.\hfill{} {[}6{]}
\item After the system is implemented, maintenance will be required. 

Name and describe \textbf{two} types of maintenance. For each type,
give an example for the swipe card system. \hfill{}{[}6{]}
\item Describe a method that can be used to ensure that only the office
staff can change the system and only the principal can view confidential
reports. \hfill{}{[}2{]}
\item The principal is considering expanding the use of the swipe card system
to record attendance in classes. 

Describe \textbf{one} disadvantage of this proposal and suggest a
more reliable method.\hfill{} {[}2{]}
\end{enumerate}