\item \textbf{{[}JJC/PRELIM/9597/2018/P1/Q4{]} }

Rock Paper Scissors is a well-known hand game played between two players,
whom we shall call P1 and P2. For each round, each player simultaneously
forms one of three signs with an outstretched hand. Rock (represented
by \textquotedbl 0\textquotedbl ), scissors (represented by \textquotedbl 2\textquotedbl )
and paper (represented by \textquotedbl 5\textquotedbl ).

Program \texttt{get\_round\_winner(p1\_hand, p2\_hand)} that decides
who wins from the hand signs of P1 and P2. If P1 wins, the function
returns 1. If P2 wins, the function returns 2. If the game is a draw,
the function returns 0.

Sample Execution:

\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{get\_round\_winner (\textquotedbl 2\textquotedbl , \textquotedbl 5\textquotedbl )
\# scissors vs paper - P1 wins}

\texttt{>\textcompwordmark >\textcompwordmark > 1}

\texttt{get\_round\_winner (\textquotedbl 2\textquotedbl , \textquotedbl 0\textquotedbl )
\# scissors vs rock - P2 wins }

\texttt{>\textcompwordmark >\textcompwordmark > 2 }

\texttt{get\_round\_winner (\textquotedbl 2\textquotedbl , \textquotedbl 2\textquotedbl )
\# scissors vs scissors - Draw}

\texttt{>\textcompwordmark >\textcompwordmark > 0}%
\end{minipage}

\subsection*{Task 4.1 }

Write program code for the function\texttt{ get\_round\_winner}.

\subsection*{Evidence 16: }

Program code for \textbf{Task 4.1}.\hfill{} {[}4{]}

P1 and P2 played a game of Rock Paper Scissors over a few rounds.
The winner is the player who wins more rounds than he losses. A draw
occurs if there is no winner. The hand signs of each player for the
game are represented as a string of \textquotedbl 0\textquotedbl ,
\textquotedbl 2\textquotedbl{} and \textquotedbl 5\textquotedbl .
For example, \textquotedbl 205\textquotedbl{} represents playing
scissors in the first round, rock in the second, and paper in the
third. 

Program \texttt{get\_game\_winner(p1\_hands, p2\_hands)} that decides
who wins the game from a sequence of hand signs from P1 and P2. If
P1 wins, return 1, if P2 wins, return 2, if the game is a draw, return
0. You must use \texttt{get\_round\_winner}. You may assume that \texttt{p1\_hands}
and \texttt{p2\_hands} are strings of the same length containing only
\textquotedbl 0\textquotedbl , \textquotedbl 2\textquotedbl{} and
\textquotedbl 5\textquotedbl . 

Sample Execution:

\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{get\_game\_winner (\textquotedbl\textquotedbl , \textquotedbl\textquotedbl )
\#no hand played, game ends in a draw}

\texttt{>\textcompwordmark >\textcompwordmark > 0}

\texttt{get\_game\_winner (\textquotedbl 205\textquotedbl , \textquotedbl 520\textquotedbl )
\#P1 wins all 3 rounds, P1 wins }

\texttt{>\textcompwordmark >\textcompwordmark > 1 }

\texttt{get\_game\_winner (\textquotedbl 22222\textquotedbl , \textquotedbl 50505\textquotedbl )
\#P1 wins}

\texttt{>\textcompwordmark >\textcompwordmark > 1 }

\texttt{get\_game\_winner (\textquotedbl 2050\textquotedbl , \textquotedbl 0255\textquotedbl )
\#P2 wins }

\texttt{>\textcompwordmark >\textcompwordmark > 2 }

\texttt{get\_game\_winner (\textquotedbl 52025\textquotedbl , \textquotedbl 52025\textquotedbl )
\#Draw }

\texttt{>\textcompwordmark >\textcompwordmark > 0 }%
\end{minipage}

\subsection*{Task 4.2 }

Write program code for the function \texttt{get\_game\_winner}. 

\subsection*{Evidence 17: }

Program code for Task 4.2. \hfill{}{[}6{]}

P1 and P2 would like a more interesting interface where rows and columns
display the game played. \textbf{Each game has four rounds} and the
\textbf{overall result} (\textquotedblleft P1 wins\textquotedblright ,
\textquotedblleft P2 wins\textquotedblright{} or \textquotedblleft Draw\textquotedblright )
\textbf{will be displayed when the game is over}. 

Here is a sample screenshot of the first turns taken by player. 

\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{Round ~~~~~~~P1 ~~~~~~~P2 ~~~~~~~Round
Winner}

\texttt{1 ~~~~~~~~~~~- ~~~~~~~~- ~~~~~~~~- }

\texttt{2 ~~~~~~~~~~~- ~~~~~~~~- ~~~~~~~~- }

\texttt{3 ~~~~~~~~~~~- ~~~~~~~~- ~~~~~~~~- }

\texttt{4 ~~~~~~~~~~~- ~~~~~~~~- ~~~~~~~~- }

\texttt{Player's 1 turn.}

\texttt{Enter Rock (0), Paper (5) or Scissors (2): 2}

\texttt{Round ~~~~~~~P1 ~~~~~~~P2 ~~~~~~~Round
Winner}

\texttt{1 ~~~~~~~~~~~S ~~~~~~~~- ~~~~~~~~- }

\texttt{2 ~~~~~~~~~~~- ~~~~~~~~- ~~~~~~~~- }

\texttt{3 ~~~~~~~~~~~- ~~~~~~~~- ~~~~~~~~- }

\texttt{4 ~~~~~~~~~~~- ~~~~~~~~- ~~~~~~~~- }

\texttt{Player's 2 turn.}

\texttt{Enter Rock (0), Paper (5) or Scissors (2): 0}

\texttt{Round ~~~~~~~P1 ~~~~~~~P2 ~~~~~~~Round
Winner}

\texttt{1 ~~~~~~~~~~~S ~~~~~~~~R ~~~~~~~~P2 }

\texttt{2 ~~~~~~~~~~~- ~~~~~~~~- ~~~~~~~~- }

\texttt{3 ~~~~~~~~~~~- ~~~~~~~~- ~~~~~~~~- }

\texttt{4 ~~~~~~~~~~~- ~~~~~~~~- ~~~~~~~~- }%
\end{minipage}

\subsection*{Task 4.3 }

Write program code for the game described. Implement using \textbf{modularity}
and\textbf{ 2D array}. Include function \texttt{validate()} to ensure
the player chooses \texttt{0}, \texttt{2} or \texttt{5}. Prompt the
player to re-enter if input is invalid. 

\subsection*{Evidence 18: }

Program code for Task 4.3.\hfill{} {[}10{]}

\subsection*{Evidence 19: }

Design four appropriate test cases for the program. Present them in
a table format. \hfill{}{[}4{]}

\subsection*{Evidence 20: }

Run your program and produce screenshots for a game which ends in
a draw and another game which P1 wins.\hfill{} {[}2{]}