\item \textbf{{[}ALVL/9597/2018/P1/Q1{]} }

A program is required to input and process the number of steps taken
by members of a walking club each week. The number of steps taken
by each member is an integer in the range 0 to 100000. 

Each week, the \textquotedblleft Star of the Week\textquotedbl{} is
the member who has taken the greatest number of steps. 

The name and number of steps taken by the \textbf{previous} week's
\textquotedbl Star of the Week\textquotedbl{} are stored in the text
file, \texttt{STAR.TXT}. 

The program specification is as follows: 
\begin{itemize}
\item Input \textbf{up to} 10 names and the number of steps each has taken.
Assume that each number of steps is unique. 
\item Find the walker who has taken the greatest number of steps from this
data. 
\item Read the data about the previous \textquotedblleft Star of the Week\textquotedblright{}
from the text file \texttt{STAR. TXT}. 
\item Display a message on screen to show the previous star of the week
\textbf{and} the new star of the week, each with their number of steps.
For example, 

\texttt{Last week, Jenny Smith was 'Star of the Week' with 75827 steps
taken. }

\texttt{This week, Vanessa Lim is 'Star of the Week' with 67152 steps
taken. }
\item Update the text file, \texttt{STAR.TXT}, with the details of the new
\textquotedbl Star of the Week\textquotedblright . 
\end{itemize}

\subsubsection*{Task 1.1}

Write program code for this task that includes validation of data
entered.

\subsubsection*{Evidence 1}

Your program code. \hfill{}{[}8{]}

The program needs to be tested with different test cases. Consider
carefully, test cases for input of names and steps. 

\subsubsection*{Task 1.2}

Copy the table with the following headings. Add other test cases to
the table. One type of test case has already been added to the table.
\begin{center}
\begin{tabular}{|l|l|l|}
\hline 
\hspace{0.05\columnwidth}\textbf{Test case} & \textbf{Purpose of test data} & \textbf{Expected results}\tabularnewline
\hline 
Yi Ling Aw, 10232 & Test the maximum of 10 values & 10 values entered and star of\tabularnewline
Ryan Batisah, 42231 & entered into the program. & the week is Vanessa Lim with\tabularnewline
Lee Casmir, 35020 &  & 67152 steps taken.\tabularnewline
Daniel Bennett, 60192 &  & \tabularnewline
Sarah Heng Chee, 29389 &  & \tabularnewline
Vanessa Lim, 67152 &  & \tabularnewline
Wong Yip, 53231 &  & \tabularnewline
Rin Xie, 34200 &  & \tabularnewline
Tin Wee, 49480 &  & \tabularnewline
David Bala, 32010 &  & \tabularnewline
\hline 
\end{tabular}
\par\end{center}

\subsubsection*{Evidence 2}

Completed table with other test cases added. \hfill{}{[}4{]}

\subsubsection*{Task 1.3}

Use \textbf{three} of the test cases in the table, and produce a screenshot
for each.

\subsubsection*{Evidence 2}

Three screenshots of test cases.\hfill{}{[}3{]}