\item \textbf{{[}DHS/PRELIM/9597/2018/P2/Q6{]} }

The following figure shows the partial contents of an unnormalised
relational database table for library book loans by an amateur database
administrator. 
\noindent \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline 
CallNo & Title & Author & PublisherID & PublisherName & BorrowerID & BorrowerName & Email & LoanDate\tabularnewline
\hline 
A2345 & Superhuman & Peter Smith & P0928 & Healthy Global & X894 & Robert Lim & roblim@gmail.com & 20181004\tabularnewline
\hline 
A1133 & Agile Methodology & Sophia Jones & P7823 & CS Books & X894 & Robert Lim & roblim@gmail.com & 20181004\tabularnewline
\hline 
B5104 & Python Advanced & Zen Wang & P8246 & Make It Harder & Y532 & Mary Tan & maryt@yahoo.com & 20181007\tabularnewline
\hline 
A2257 & Computer Science & Berry Mile & P8246 & Make It Harder & X451 & Ben Neo & benn@gmail.com & 20181007\tabularnewline
\hline 
B7513 & Alibaba & Jacky Ma & P3245 & Ali Pub  & X451 & Ben Neo & benn@gmail.com & 20181007\tabularnewline
\hline 
\end{tabular}
\par\end{center}

\begin{enumerate}
\item Give \textbf{two} potential anomalies that can occur with this design.
\hfill{}{[}2{]}
\item Give \textbf{two} advantages of normalisation. \hfill{}{[}2{]}
\item Give the table specification in 
\begin{enumerate}
\item 1NF
\item 2NF
\item 3NF \hfill{}{[}6{]}
\end{enumerate}
\item Draw an E-R diagram to represent your normalised design.\hfill{}
{[}3{]}
\item The following figure shows the notification email sent to the borrower
upon successful loan of library books.

\noindent\fbox{\begin{minipage}[t]{1\columnwidth - 2\fboxsep - 2\fboxrule}%
\texttt{Oct 4, 2018, 6:52 PM }

\texttt{From: NLB <helpdesk@nlb.gov.sg> }

\texttt{To: roblim@gmail.com}

\bigskip{}

\texttt{Dear Robert Lim}

\bigskip{}

\texttt{Thank you for using NLB's e-notification service through email,
a free service available to all library members.}

\bigskip{}

\texttt{This notification service confirms the number of items you
have borrowed at the library book borrowing station.}

\bigskip{}

\texttt{You have borrowed 2 item(s) at 18:52 on 4 Oct 2018 at Serangoon
Public Library:}

\bigskip{}

\texttt{1. Superhuman }

\texttt{~~~Due on: 25 October 2018}

\bigskip{}

\texttt{2. Agile Methodology }

\texttt{~~~Due on: 25 October 2018}

\bigskip{}

\texttt{You may also check your updated account status at http://www.nlb.gov.sg}%
\end{minipage}}

Describe how the customised contents of the notification email are
generated from the database. You may assume that the default loan
period is 21 days.\hfill{} {[}3{]}
\end{enumerate}