\item \textbf{{[}JJC/PRELIM/9597/2018/P1/Q1{]} }

A web log, \texttt{WEBLOG.txt}, keeps track of the date and time the
server is being accessed, as well as the client that accessed it.
The client is identified by either the host name or internet address.
The format of \texttt{WEBLOG.txt} is as follows: 
\noindent \begin{center}
\texttt{<host name>|<DD/MMM/YYYY:HH:MM:SS> }
\par\end{center}

\noindent \begin{center}
\textbf{or }
\par\end{center}

\noindent \begin{center}
\texttt{<internet address>|<DD/MMM/YYYY:HH:MM:SS>} 
\par\end{center}

Below is a sample of \texttt{WEBLOG.txt}: 

\noindent\fbox{\begin{minipage}[t]{1\columnwidth - 2\fboxsep - 2\fboxrule}%
\texttt{199.72.81.55|01/Jul/2018:08:00:01 }

\texttt{jurongjc.moe.edu.sg|01/Jul/2018:09:08:06 }

\texttt{199.120.110.21|01/Jul/2018:11:30:09 }

\texttt{trioon.com|01/Jul/2018:11:45:58 }%
\end{minipage}}

A client address (host name or internet address) can appear in \texttt{WEBLOG.txt}
multiple times. Similarly, the date it accessed the server can be
duplicated because it can access the server more than once in a day. 

A summary report, \texttt{SUMMARYREPORT.txt}, is to be generated to
list the unique clients (hosts name/internet address) and their corresponding
dates. Below is a sample of \texttt{SUMMARYREPORT.txt}: 

\noindent\fbox{\begin{minipage}[t]{1\columnwidth - 2\fboxsep - 2\fboxrule}%
\texttt{199.72.81.55~~~~~~~ 01/Jul/2018,03/Jul/2018,04/Jul/2018 }

\texttt{jurongjc.moe.edu.sg 01/Jul/2018,02/Jul/2018,03/Jul/2018 }

\texttt{trioon.com ~~~~~~~~~01/Jul/2018,05/Jul/2018}%
\end{minipage}} 

\subsection*{Task 1.1 }

Write a procedure \texttt{readLog()} to read \texttt{WEBLOG.txt}.
Use suitable data structure(s), and prepare the log information to
create \texttt{SUMMARYREPORT.txt}.

\subsection*{Evidence 1: }

Your \texttt{readLog()} procedure code.\hfill{} {[}6{]}

\subsection*{Task 1.2 }

Write a procedure \texttt{processLog()} to generate \texttt{SUMMARYREPORT.txt}.

\subsection*{Evidence 2: }

Your \texttt{processLog()} procedure code.\hfill{} {[}4{]}

\subsection*{Evidence 3:}

Screenshot of \texttt{SUMMARYREPORT.txt} after running the program.\hfill{}
{[}1{]}

\subsection*{Task 1.3 }

Add code to your Task 1.2 program to display the highest number of
days the server was accessed by any client, and the corresponding
client(s). Below is a sample of screen output:

\noindent\fbox{\begin{minipage}[t]{1\columnwidth - 2\fboxsep - 2\fboxrule}%
\texttt{>\textcompwordmark >\textcompwordmark > Highest frequency
(days): 3 }

\texttt{>\textcompwordmark >\textcompwordmark > Accessed by: }

\texttt{>\textcompwordmark >\textcompwordmark > 199.72.81.55 }

\texttt{>\textcompwordmark >\textcompwordmark > jurongjc.moe.edu.sg }%
\end{minipage}}

\subsection*{Evidence 4:}

Your program code for \textbf{Task 1.3}.\hfill{} {[}4{]}

\subsection*{Evidence 5:}

Screenshot of the program output.\hfill{} {[}1{]}