\item \textbf{{[}DHS/PRELIM/9597/2018/P1/Q4{]} }

The Romans had their own system of number representation which used
a sequence of upper case letter characters to represent a number.
We shall consider the denary number 1 to 20 only. 

The following letters represent each of the values shown: 
\noindent \begin{center}
\begin{tabular}{|c|c|}
\hline 
Roman Numeral  & Represents\tabularnewline
\hline 
I & One\tabularnewline
\hline 
V & Five\tabularnewline
\hline 
X & Ten\tabularnewline
\hline 
L & Fifty\tabularnewline
\hline 
\end{tabular}
\par\end{center}

A number is always written with the smallest number of characters,
with the letters in sequence starting with the character with the
largest value. 
\begin{itemize}
\item For example, 6 is written \texttt{VI} (not \texttt{IIIIII}) 
\end{itemize}
The exceptions to this sequence are as follows: 
\begin{itemize}
\item one less than 5 -{}- which is written as \texttt{IV}
\item one less than ten -{}- which is written as \texttt{IX} 
\item ten less than fifty -{}- which is written as \texttt{XL} 
\end{itemize}

\subsection*{Task 4.1}

Write program code with the following specification: Input a denary
integer number in the range 1 to 20 Validate the input Calculate the
Roman numeral representation (write this code as a function) Output
the Roman number. 

\subsection*{Evidence 21 }

Your program code. \hfill{}{[}6{]}

\subsection*{Task 4.2 }

Draw up a list of \textbf{three} suitable tests and provide screenshot
evidence for your testing.

\subsection*{Evidence 22 }

Annotated screenshots for each test data run.\hfill{} {[}3{]}

\subsection*{Task 4.3}

Write additional program code with appropriate data validation for
the following specification:
\begin{itemize}
\item Input two Roman numeral numbers between 1 and 20 
\item Ouput the sum of the numbers as a Roman numeral number.
\end{itemize}

\subsection*{Evidence 23 }

Your program code.\hfill{} {[}8{]}

\subsection*{Task 4.4 }

Draw up a list of \textbf{three} suitable tests and provide screenshot
evidence for your testing. 

\subsection*{Evidence 24 }

Annotated screenshots for each test data run. \hfill{}{[}3{]}