\item \textbf{{[}RVHS/PRELIM/9597/2019/P2/Q8{]} }

The school library currently stores their data in flat files. These
files contain information about students, books and their loaning
details. 

Using examples from the school\textquoteright s flat files to illustrate
your answers.
\begin{enumerate}
\item Explain how data inconsistency could arise.\hfill{} {[}2{]}
\item Explain why data privacy could be a potential concern.\hfill{} {[}2{]}
\item Explain the definition of Primary Key in a relational database. \hfill{}{[}2{]}
\end{enumerate}
A book can be borrowed by any student, and a student can borrow any
book. Students need to fill up a loaning record form each time he/she
wants to borrow a book. A student is entitled to borrow up to 5 books
each time using the same loaning record form.

The decision has been made to create a relational database for the
library loaning system.
\begin{enumerate}
\item[(d)]  Identify the necessary tables and draw an E-R diagram to show the
relationships between these tables. {[}4{]}
\item[(e)]  For each table specify the attributes (fields) required and state
suitable primary keys and foreign key relationships. State necessary
legends if you are using symbols to represent the primary and foreign
keys. {[}7{]}
\end{enumerate}
The following table is generated for students\textquoteright{} reference
regarding their loaning details.

\begin{tabular}{|l|l|l|l|}
\hline 
\textbf{Student Name:} & Xiao Ming  & \textbf{Class: } & 19J08\tabularnewline
\hline 
 &  &  & \tabularnewline
\hline 
\textbf{Book Name} & \textbf{Author} & \textbf{Loan Date} & \textbf{Due Date}\tabularnewline
\hline 
A Brief History of Time & Stephen Hawking & 05 Aug 2019 & 30 Aug 2019\tabularnewline
\hline 
Spider Man Comics & Stan Lee & 29 Aug 2019 & 20 Sep 2019\tabularnewline
\hline 
\end{tabular}
\begin{enumerate}
\item[(f)]  To create the report \texttt{StudentName} and \texttt{StudentClass}
are used. Name other fields that the database uses to produce this
report.\hfill{}{[}4{]}
\end{enumerate}
Beside the database design, you are also in charge of creating an
online loaning form.
\begin{enumerate}
\item[(g)]  Design and draw a webpage layout for the auto loaning interface
for the new system. Identify and briefly explain your design considerations
for the various features which aid users to input valid data entries.
\hfill{}{[}4{]}
\item[(h)]  Some students use their handphones to snap photos of tables and
charts from the books they borrowed and use them for their research
projects. Explain what potential issues may arise and suggest alternate
ways which students can adopt.\hfill{} {[}3{]}
\end{enumerate}