\item \textbf{{[}HCI/PRELIM/9597/2019/P2/Q1{]} }

A bookshop wishes to expand its business from a brick and mortar shop
to allow for online sales. A software company has been engaged by
the bookshop to develop the online sales system. 
\begin{enumerate}
\item The analyst decides to adopt a top-down approach to the design. What
are the advantages of using top-down design to solve complex problems?\hfill{}
{[}3{]} 
\end{enumerate}
The project manager decides to use some project management tool in
the planning of the project. Below is the list of activities along
with their required time for completion.
\noindent \begin{center}
\begin{tabular}{|c|c|c|}
\hline 
Activity & Expected completion time (day) & Preceded by\tabularnewline
\hline 
\hline 
A & 2 & -\tabularnewline
\hline 
B & 3 & A\tabularnewline
\hline 
C & 1 & B\tabularnewline
\hline 
D & 3 & B\tabularnewline
\hline 
E & 4 & C\tabularnewline
\hline 
F & 3 & D\tabularnewline
\hline 
G & 2 & A\tabularnewline
\hline 
H & 5 & G\tabularnewline
\hline 
I & 3 & E, F, H\tabularnewline
\hline 
\end{tabular}
\par\end{center}
\begin{enumerate}
\item[(b)]  Construct the PERT chart for the activities, indicating the earliest
start time and latest start time of each activity. \hfill{}{[}3{]}
\item[(c)]  Which tasks are on the critical path of the Program Evaluation and
Review Technique (PERT) chart? \hfill{}{[}1{]}
\item[(d)]  What is the slack time for Task C and G? \hfill{}{[}2{]}
\item[(e)]  The person working on Task C tells the project manager he cannot
start work until one day after the scheduled starting date. What impact
would this have on the completion date of the project? Why?\hfill{}
{[}2{]}
\item[(f)]  Task A will be delayed by 2 days for some reason. If the project
manager still wants to finish the project within the original time
frame, he will need to shorten the time for one or more of the tasks.
What steps can he take to reduce the number of days allocated to a
task? \hfill{}{[}2{]}
\item[(g)]  The project manager decides to reduce the time needed for Tasks
D and F by one day each. How effective will this reduction be in achieving
his aim of maintaining the original finish time for the project? What
can he do for it to be more effective?\hfill{} {[}2{]}
\item[(h)]  Produce a Gantt chart based on the above information. \hfill{}{[}2{]}
\item[(i)]  Give \textbf{one} reason why a Gantt chart may be preferred over
a PERT chart.\hfill{} {[}1{]}
\end{enumerate}