\item \textbf{{[}JPJC/PRELIM/9597/2019/P1/Q2{]} }

The incomplete pseudocode function below takes in an array as input.
The array will then be sorted in ascending order and the results will
be returned. Note that the start index of the array is 1. 

\noindent %
\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{FUNCTION SomeSort(SomeList : ARRAY) }

\texttt{\qquad{}FOR Pointer \textleftarrow{} 2 TO NumberOfItems }

\texttt{\qquad{}\qquad{}ItemToBeInserted \textleftarrow{} SomeList{[}Pointer{]} }

\texttt{\qquad{}\qquad{}CurrentItem \textleftarrow{} Pointer \textendash{}
1 }

\texttt{\qquad{}\qquad{}WHILE(SomeList{[}CurrentItem{]}>ItemToBeInserted
AND CurrentItem>0) }

\texttt{\qquad{}\qquad{}\qquad{}SomeList{[}CurrentItem+1{]} \textleftarrow{}
SomeList{[}CurrentItem{]} }

\texttt{\qquad{}\qquad{}\qquad{}CurrentItem \textleftarrow{} CurrentItem
- 1 }

\texttt{\qquad{}\qquad{}ENDWHILE}

\texttt{\qquad{}\qquad{}............... $\mathtt{A}$............... }

\texttt{\qquad{}ENDFOR }

\texttt{\qquad{}RETURN ARRAY}

\texttt{ENDFUNCTION }%
\end{minipage}

\subsection*{Task 2.1 }

Complete the missing line and write program code to implement the
complete function. Sort the array given in the file \texttt{NUMBERS.txt}.
You may copy and paste the array into your program code. 

\subsection*{Evidence 3 }
\begin{itemize}
\item Your program code. 
\item Screenshot showing the array before and after running the function.\hfill{}
{[}7{]}
\end{itemize}

\subsection*{Task 2.2 }

Write a bubble sort function that takes an array, sorts the array
and returns the array. 

\subsection*{Evidence 4 }

Your bubble sort function.\hfill{} {[}4{]}

\subsection*{Task 2.3 }

Amend your program code in both functions to count and display the
number of comparisons made when sorting the array. 

\subsection*{Evidence 5 }
\begin{itemize}
\item Your amended program code. 
\item Screenshot of running both sorting functions with number of comparisons
displayed.\hfill{} {[}4{]}
\end{itemize}