\item \textbf{{[}YIJC/PRELIM/9597/2019/P1/Q4{]} }

Minesweeper is a type of single-player puzzle game in which the player
continuously selects a cell in a square grid. Each cell contains either
a bomb or a value showing the number of bombs in the neighbouring
cell. (Neighbouring cells are those adjacent horizontally, vertically
or diagonally.)

If the player selects a cell that is a bomb, it \textquoteleft explodes\textquoteright{}
and he loses the game. The number of cells the player has selected
without exploding a bomb will be the player\textquoteright s score.

You are required to write a program code to generate a minesweeper
grid, randomly position the bombs and populate all the other cells
with the values indicating the number of bombs in the neighbouring
cells. Without revealing the minesweeper grid to the player, the program
should prompt the player to select the cells one by one. His score
will be the number of cells opened before hitting a bomb. 
\noindent \begin{center}
\begin{minipage}[t]{0.25\columnwidth}%
\texttt{X 2 1 1 }

\texttt{1 3 X 2 }

\texttt{0 2 X 3 }

\texttt{0 1 2 X }%
\end{minipage}
\par\end{center}

\subsection*{Task 4.1: }

Write a program code to generate and display an empty square grid
of size $n$, ie $n$ rows by $n$ columns. The minesweeper grid for
$n=5$ is as shown below: 
\noindent \begin{center}
\begin{minipage}[t]{0.25\columnwidth}%
\texttt{0 0 0 0 0 }

\texttt{0 0 0 0 0 }

\texttt{0 0 0 0 0 }

\texttt{0 0 0 0 0}

\texttt{0 0 0 0 0 }%
\end{minipage}
\par\end{center}

Your code should use a suitable data structure and fixed loop(s) to
display the grid.

\subsection*{Evidence 4.1: }

Your program code and screenshot of an empty grid of size 5.\hfill{}
{[}3{]}


\subsection*{Task 4.2: }

Write a program code to randomly place a bomb, represented by \textquotedbl X\textquotedbl ,
within the grid. Populate all the neighbouring cells by increasing
their values to 1 to indicate the presence of this one bomb in the
neighbourhood. 

\subsection*{Evidence 4.2: }

Your program code and two different screenshots of the grid ($n=5$).
\hfill{}{[}5{]}

\subsection*{Task 4.3: }

Modify the code written in Task 4.2 to randomly place two bombs within
the grid. Populate all the neighbouring cells with the correct values
to indicate the presence of the bombs in the neighbourhood. 

\subsection*{Evidence 4.3: }

Your program code and the screenshot of the grid ($n=5$) with 2 bombs.\hfill{}
{[}4{]}

\subsection*{Task 4.4: }

Modify the code written in Task 4.3 to generate $k$ numbers of bombs
within a grid of size $n$ and correctly display all the values in
the neighbouring cells surrounding the bombs. 

\subsection*{Evidence 4.4: }

Your program code and the screenshots of the minesweeper grids for
the following levels of difficulty. 
\begin{itemize}
\item Beginner (grid size $n=5$; no. of bombs $k=3$)
\item Intermediate (grid size $n=6$; no. of bombs $k=8$)
\item Expert (grid size $n=8$; no. of bombs $k=20$) {[}8{]}
\end{itemize}

\subsection*{Task 4.5: }

Write a program code to play the minesweeper game. Your code will:
\begin{itemize}
\item prompt the player to select the level of difficulty
\item generate the Minesweeper grid 
\item display a \textquotedblleft blank\textquotedblright{} grid with \textquoteleft -\textquoteright{}
for each of the cell prompt the player to input the coordinates of
a cell he wishes to open 
\begin{itemize}
\item If the opened cell is a bomb (\textquotedblleft X\textquotedblright ),
declare \textquotedblleft Game Over!\textquotedblright , show the
grid and display the player\textquoteright s score.
\item If the opened cell is not a bomb, show the updated grid with the opened
cell, increase the player\textquoteright s score by 1 and continue
with the game.
\end{itemize}
\item declare \textquotedblleft You have Won!\textquotedblright{} when the
player has opened all the possible cells and display the player\textquoteright s
score. 

{[}Sample screenshot of a typical game{]}: 

\noindent %
\begin{minipage}[t]{0.5\columnwidth}%
\texttt{Enter your cell you want to open:}

\texttt{X (1 to 5) : 2}

\texttt{Y (1 to 5) : 3}

\texttt{\_ \_ \_ \_ \_}

\texttt{\_ \_ 1 \_ \_}

\texttt{0 \_ \_ \_ \_}

\texttt{\_ \_ 1 \_ \_}

\texttt{\_ \_ \_ \_ \_}

\texttt{Your score is : 3}%
\end{minipage}%
\begin{minipage}[t]{0.5\columnwidth}%
\texttt{Enter your cell you want to open:}

\texttt{X (1 to 5) : 2}

\texttt{Y (1 to 5) : 4}

\texttt{X 1 1 1 1}

\texttt{1 1 1 X 1}

\texttt{0 0 1 1 1}

\texttt{0 1 1 1 0}

\texttt{0 1 X 1 0}

\texttt{Game over! You've hit the bomb at : (2,4).}

\texttt{Your score is : 3}

\texttt{Do you want to try again?}%
\end{minipage}
\end{itemize}

\subsection*{Evidence 4.5:}

Your program code and a screenshot of a game. \hfill{}{[}10{]}