\item \textbf{{[}DHS/PRELIM/9597/2019/P2/Q6{]} }

BuildingBloCS is Singapore's first/only/largest by Computing students
for Computing students and beyond national Computing education outreach
programme. In 2019, it comprises a series of workshops, talks, games,
projects showcase, programming quizzes, lucky draws and more (media
and entertainment very important). 

The organisers would like to apply what they learned in Computing
to manage workshop information using a relational database. 
\begin{itemize}
\item Each participant can register for one or more workshops 
\item Each workshop is conducted by one or more instructors 
\item Each workshop is also facilitated by one or more facilitators 
\end{itemize}
Due to Personal Data Protection Act (PDPA), it is decided to use an
alternative unique identifier as the primary key instead of collecting
participants' NRICs/FINs.

The normalised design requires a number of tables.
\begin{enumerate}
\item Draw an Entitiy-Relationship (E-R) diagram that shows these tables
and the relationships between them. \hfill{} {[}4{]}
\item Suggest and justify a suitable primary key candidate other than NRIC/FIN.
\hfill{} {[}2{]}
\item A table description can be expressed as:

\texttt{TableName(Attribute1, Attribute2, Attribute3, \dots )}

The primary key is indicated by underlining one or more attributes.

Derive the table descriptions for the tables. \hfill{}{[}6{]}
\item There are some fields with missing or null values. Explain how these
arise and how a Database Management System (DBMS) may provide facilities
to ensure the information is appropriately managed. \hfill{}{[}3{]}
\end{enumerate}