\item \textbf{{[}DHS/PRELIM/9597/2019/P1/Q1{]} }

The file \texttt{IOI19.TXT} stores the scoreboard of the 31st International
Olympiad in Informatics (IOI) held in Baku, Azerbaijan from 4 to 11
August 2019. The first line contains the header with contestant's
rank, name, team (country), and overall score. The remaining lines
contain the corresponding data. IOI 2019 eventually awarded 28 Gold,
54 Silver and 81 Bronze medals. A country typically sends up to 4
contestants to participate in IOI. 

\subsection*{Task 1.1 }

Determine the top 3 teams in the competition and display their country
names as well as the number of Gold, Silver and Bronze medals attained.
Teams which are tied will be ordered by their country names in alphabetical
order and will share the same rank. 

Sample output: 

\texttt{Top 3 teams: }

\texttt{1 ABC 4G }

\texttt{2 DEF 3G1S }

\texttt{2 GHI 3G1S }

\texttt{4 JKL 2G1S1B }

\texttt{4 MNO 2G1S1B }

\subsection*{Evidence 1 }

Program code. \hfill{}{[}9{]}

\subsection*{Evidence 2 }

Screenshot. \hfill{} {[}1{]}

\subsection*{Task 1.2 }

Write program code to prompt a user to enter a team name and display
the results of its participants. Participants who did not receive
a medal will be denoted with \texttt{P}. The program will terminate
when a user enters the text string \texttt{'ZZZ'} (without the quotes). 

Sample interaction: 

\texttt{Enter team: SGP }

\texttt{Eu-Shaun Leong G }

\texttt{Lee Jeffrey Chun Hean S }

\texttt{Benson Zhan Li Lin B }

\texttt{Daniel Zhenghao Choo P }

\texttt{Enter team: ZZZ }

\texttt{Bye }

\subsection*{Evidence 3}

Program code. \hfill{} {[}4{]}

\subsection*{Evidence 4 }

Screenshot. \hfill{}{[}1{]}