\item \textbf{{[}JPJC/PRELIM/9597/2019/P2/Q5{]} }

With reference to \textbf{Question 1}, a server--based ordering system
will be implemented in XFurniture.

Local Area Network (LAN) will be used for the staff and customers.
\begin{enumerate}
\item Explain the meaning of a protocol for communication within the LAN.
\hfill{}{[}1{]}
\item State the purposes of switches and routers in a network. \hfill{}{[}4{]}
\item Explain the differences between using packet switching and circuit
switching in the transmission of a message. \hfill{} {[}3{]}
\item The LAN is connected to the Internet. Discuss the social and ethical
effects of allowing staff to have unrestricted access to the Internet.
\hfill{}{[}4{]}
\item Customers are now able to order furniture online after logging in
to the XFurniture online system. 
\begin{enumerate}
\item Explain why authentication techniques are necessary. \hfill{} {[}2{]}
\item Explain \textbf{two} methods for ensuring security of a network application.
\hfill{}{[}2{]}
\item A security policy is a formalised statement that defines how security
will be implemented within XFurniture. Explain why staff members are
required to know the need for privacy and integrity of data. \hfill{}{[}2{]}
\end{enumerate}
\item Explain why XFurniture has chosen to implement their server--based
ordering system over the intranet. \hfill{}{[}4{]}
\item An alternative to a server--based ordering system is to subscribe
the services of cloud computing. State the \textbf{three} services
provided by cloud computing, and explain how they can benefit XFurniture.
\hfill{} {[}6{]}
\end{enumerate}