\item \textbf{{[}HCI/PRELIM/9597/2019/P1/Q1{]} }

The manager of a private carpark wants to process the daily data of
people using the carpark. The carpark is open from 8am to 11pm and
the carpark charge is as follows:
\begin{itemize}
\item Before 5pm: \$1.50 per hour or part thereof 
\item After 5pm, \$3.00 per entry regardless of the duration
\end{itemize}
However, if a car enters before 5pm and leaves after 5pm, the charge
involves both rules. For example, if the car stays in the carpark
from 2.45pm to 6.30pm, it is broken down to 2 hours 15 minutes before
5pm and 1 hour 30 minutes after 5pm. Hence the charge will be \$1.50
{*} 3 + \$3.00 = \$7.50. 

Each day the carpark electronic system generates a file\texttt{ CARPARK.txt}.
Each record in the file has the following format:
\noindent \begin{center}
\texttt{<CARPLATE NUMBER>,<START TIME>,<END TIME>}
\par\end{center}

For example, \texttt{SLX2315A,0940,1415} means that a car with car
plate number SLX2315A entered the carpark at 9.40am and left at 2.15pm. 

You are \textbf{not} allowed to use any built-in functions for time
processing. 

\subsection*{Task 1.1 }

Write program code for the \texttt{Price} function using the following
specification:
\noindent \begin{center}
\texttt{FUNCTION Price (start: STRING, end: STRING) : FLOAT}
\par\end{center}

The function has two string parameters \texttt{start}, \texttt{end}
which refers to the start and end time when the car parked. The function
returns the carpark charge as a float. 

\subsection*{Evidence 1 }

Your program code.\hfill{} {[}5{]}

\subsection*{Task 1.2 }

Write a program code to perform the following task for the manager:
\begin{itemize}
\item Read data from \texttt{CARPARK.txt }
\item Write all the car plate numbers and corresponding carpark charges
to another file \texttt{CHARGE.txt}, in the following format: 
\noindent \begin{center}
\texttt{<CARPLATE NUMBER>,<CARPARK CHARGE>}
\par\end{center}

\noindent \begin{center}
\texttt{<CARPLATE NUMBER>,<CARPARK CHARGE>}
\par\end{center}
\item Output the total charges for the day
\end{itemize}

\subsection*{Evidence 2 }

Your program code.\hfill{} {[}7{]}

\subsection*{Evidence 3}

One screenshot showing the program output and contents of \texttt{CHARGE.txt}
from running the program.\hfill{} {[}3{]}