\item \textbf{{[}ALVL/9597/2019/P2/Q1{]} }

Pharmacists working in a group of pharmacies, dispense medicine to
patients who present to them a prescription written by a doctor. A
new system is to be built to allow a doctor to send prescription data
electronically to a pharmacy of the patient's choice. Patients will
either collect the medicine, or have the pharmacy deliver it to them. 

A project proposal is written and sent to doctors and pharmacy staff,
inviting each to respond within a given time. 
\begin{enumerate}
\item Give a reason why the project proposal is sent to: 
\begin{enumerate}
\item Doctors \hfill{}{[}1{]}
\item Pharmacy staff \hfill{}{[}1{]}
\end{enumerate}
\end{enumerate}
The responses from the doctors and pharmacy staff are reviewed. Invitations
are sent to doctors to find out whether they are willing to take part
in a pilot scheme. The project proposal is sent to prospective software
developers. Some of the activities involved in the project are listed
in the following table. 
\begin{center}
\begin{tabular}{|c|l|c|}
\hline 
Label & \hspace{0.25\columnwidth}Activity & Duration(Weeks)\tabularnewline
\hline 
\textbf{A} & Send project proposal  & 4\tabularnewline
\hline 
\textbf{B} & Send project proposal to pharmacy staff & 2\tabularnewline
\hline 
\textbf{C} & Discuss all the responses from A and B. and revise the proposal if
2 required & 2\tabularnewline
\hline 
\textbf{D} & Send project proposal to prospective software developers & 3\tabularnewline
\hline 
\textbf{E} & Invite doctors to be part of a pilot scheme & 2\tabularnewline
\hline 
\textbf{F} & Request quotations of cost and development time from software developers & 3\tabularnewline
\hline 
\textbf{G} & Select a software developer  & 1\tabularnewline
\hline 
\end{tabular}
\par\end{center}
\begin{enumerate}
\item[(b)] {}
\begin{enumerate}
\item Draw a Gantt chart for the activities labelled \textbf{A} to \textbf{G}.
\hfill{}{[}6{]}
\item State the estimated time taken to complete activities \textbf{A} to
\textbf{G}. \hfill{}{[}1{]}
\end{enumerate}
\end{enumerate}
In activities \textbf{A} and \textbf{B}, doctors and pharmacy staff
identified ethical and security issues that would need to be addressed. 
\begin{enumerate}
\item[(c)] {}
\begin{enumerate}
\item Describe one security issue. \hfill{}{[}2{]}
\item Describe one ethical issue. \hfill{}{[}2{]}
\end{enumerate}
\end{enumerate}
In activity \textbf{F}, quotations are received from software developers.
The lowest cost is from a developer who works alone, but demonstrates
a number of successful projects. Other software developers that employ
many staff submit more expensive quotations. 
\begin{enumerate}
\item[(d)] Explain why the group of pharmacies may decide against the single
developer. \hfill{}{[}2{]}
\end{enumerate}
An analyst from the chosen software developer reviews the current
system. 
\begin{enumerate}
\item[(e)] Give \textbf{four} methods available to the analyst to find out how
a system operates. \hfill{}{[}4{]}
\end{enumerate}
The analyst proposes that the doctors and pharmacy staff interact
with a web-based system. 
\begin{enumerate}
\item[(f)] tate the software that will be needed on the devices used by the
doctors and pharmacy staff. other than the operating system. \hfill{}{[}1{]}
\end{enumerate}
The alternative to a web-based system would be to write and install
purpose-built application software for each computer used by a doctor
or member of the pharmacy staff. 
\begin{enumerate}
\item[(g)] Describe \textbf{two} advantages to the software developer of a web-based
solution over purpose- built software running on each user's computer.
\hfill{}{[}4{]}
\end{enumerate}
Doctors may wish to write prescriptions when they visit patients in
their own home. 
\begin{enumerate}
\item[(h)] Explain \textbf{one} benefit of a web-based solution in this situation.
\hfill{}{[}2{]}
\end{enumerate}
The computers used by the doctors and pharmacy staff are clients of
the server operated by the pharmacy. Some validation is provided by
client-side scripting.
\begin{enumerate}
\item[(i)] Give \textbf{two} advantages of using this type of scripting. \hfill{}{[}2{]}
\end{enumerate}
The new system is designed. coded and tested as a number of modules.
A tester performing black-box testing on a module would need its specification. 
\begin{enumerate}
\item[(j)] Explain why the tester would not need access to the source code.
\hfill{}{[}2{]}
\item[(k)] Explain why someone designing a test strategy for white box testing
would need access to the source code. \hfill{}{[}2{]}
\item[(l)] Alpha testing is performed on the system. 

Explain the purpose of alpha testing. \hfill{} {[}2{]}
\item[(m)] The group of pharmacies is responsible for the security and integrity
of the stored data. 
\begin{enumerate}
\item Give \textbf{two }methods that could be used to ensure security of
the stored data. \hfill{}{[}2{]}
\item Give \textbf{two} methods that could be used to ensure the integrity
of the stored data. \hfill{}{[}2{]}
\end{enumerate}
\item[(n)] The group considers using either the cloud or its own server to store
data needed by the proposed system. 

Give \textbf{one} advantage and \textbf{one} disadvantage of storing
the data in the cloud. \hfill{}{[}2{]}
\end{enumerate}