\item \textbf{{[}JPJC/PRELIM/9597/2019/P2/Q1{]} }

Furniture retailer XFurniture is currently using a manual, paper-based
ordering system. 

The customer visits the show room and informs the salesperson his/her
furniture selection. After which, the salesperson asks the filing
clerk to locate the relevant paper files that contain all the necessary
details of the chosen item in the file cabinet. The files contain
the following information of a furniture item:
\begin{itemize}
\item item code 
\item description of item 
\item price of item 
\item delivery time 
\item details of the supplier
\end{itemize}
The customer pays for the purchase and the salesperson hands the original
purchase order, and a duplicate copy to the customer and the filing
clerk respectively. At the end of the day, the filing clerk will record
the total sales for the day and proceed to order the furniture from
the supplier by sending them a purchase order of the consolidated
furniture items sold for the day. 

The management of XFurniture decides to replace its current system
with a server--based ordering system. 

A system developer from an IT consultant firm is employed to carry
out the project. The first task is to write a project proposal. 
\begin{enumerate}
\item One section of the project proposal is the Problem Statement which
lists the problems in the current system. Write the Problem Statement.
\hfill{}{[}4{]}
\end{enumerate}
The system developer draws up a list of activities that will be required
for the completion of the software project:
\noindent \begin{center}
\begin{tabular}{|c|l|c|}
\hline 
Identifier & Activity & Estimated Duration (weeks)\tabularnewline
\hline 
A & Order and deliver the new database system and server & 4\tabularnewline
\hline 
B & Design and install the network infrastructure & 7\tabularnewline
\hline 
C & Order, deliver and install new PCs and printer & 9\tabularnewline
\hline 
D & est the database system, server and network & 3\tabularnewline
\hline 
E & Test the PCs with the server and network & 2\tabularnewline
\hline 
F & Copy existing sales data to the new database system & 1\tabularnewline
\hline 
G & Copy other existing PC software to the new PCs & 3\tabularnewline
\hline 
H & Test all software and database on the new PCs and server & 1\tabularnewline
\hline 
I & Train users & 2\tabularnewline
\hline 
\end{tabular}
\par\end{center}

Tasks A, B and C can be undertaken at the same time, but Task A and
Task B must be completed before Task D can commence. Tasks C and D
must be completed before Task E can begin. Task E must be completed
before Tasks F and G can start. Tasks F and G can be undertaken at
the same time, but both must be completed before Task H can commence.
Task I must follow Task H. 
\begin{enumerate}
\item[(b)]  Draw a PERT chart for this project. Provide a node key explaining
the layout and contents of the nodes used in your diagram. \hfill{}{[}4{]} 
\item[(c)]  Copy and complete the following table with the earliest and latest
start times, the earliest and latest finish times, duration, and float
time for each task. 
\noindent \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
Task & EST & LST & EFT & LFT & Duration & Float\tabularnewline
\hline 
A & 0 & 3 & 4 & 7 & 4 & 3\tabularnewline
\hline 
B &  &  &  &  & 7 & \tabularnewline
\hline 
C &  &  &  &  & 9 & \tabularnewline
\hline 
D &  &  &  &  & 3 & \tabularnewline
\hline 
E &  &  &  &  & 2 & \tabularnewline
\hline 
F & 12 & 14 & 13 & 15 & 1 & \tabularnewline
\hline 
G &  &  &  &  & 3 & \tabularnewline
\hline 
H & 15 & 15 & 16 & 16 & 1 & \tabularnewline
\hline 
I & 16 & 16 & 18 & 18 & 2 & 0\tabularnewline
\hline 
\end{tabular} 
\par\end{center}

\hfill{}{[}4{]}
\item[(d)]  State the critical path.\hfill{} {[}1{]}
\item[(e)]  State the minimum time required for the project to be completed.
\hfill{} {[}1{]}
\item[(f)]  Dummy task may be used in PERT chart. What is a dummy task? \hfill{}
{[}1{]}
\item[(g)]  Draw a Gantt chart for the same project tasks, showing each of these
tasks, all dependencies, and the duration of each task. Highlight
the critical path on the Gantt chart.\hfill{} {[}4{]}
\end{enumerate}