\item \textbf{{[}HCI/PRELIM/9597/2019/P1/Q2{]} }

When a list of integers has repeated numbers, the searching and sorting
algorithms can be different. The task is to perform an insertion sort
before a binary search is executed. 

\subsection*{Task 2.1 }

Write the program code for a procedure to implement insertion sort
in ascending order. The input parameter is a list of integers which
may have repeated numbers. 

\subsection*{Evidence 4}

Your program code.\hfill{} {[}4{]}

\subsection*{Task 2.2 }

Write the program code for a procedure to implement binary search
for a targeted integer. The input parameter is an ordered list of
integers which may have repeated numbers. The procedure outputs all
the indices at which the target appears, or \texttt{\textminus 1}
if the target is not found. 

\subsection*{Evidence 5 }

Your program code. \hfill{}{[}9{]}

\subsection*{Task 2.3 }

The file \texttt{NUMBERS.txt} contains one integer at each line. Write
a program that uses the procedures in previous tasks and performs
the following task: 
\begin{itemize}
\item Reads the text file \texttt{NUMBERS.txt}, 
\item Perform insertion sort, and outputs the list of integers in a row, 
\item Prompts the user to provide a target to be searched, 
\item Perform a binary search and output an appropriate message
\end{itemize}

\subsection*{Evidence 6 }

Your program code.\hfill{} {[}4{]}

\subsection*{Task 2.4 }

Draw up \textbf{three} suitable tests and provide screenshot evidence
for your testing. 

\subsection*{Evidence 7 }

Annotated screenshots for each test data run. \hfill{}{[}3{]}