\item \textbf{{[}HCI/PRELIM/9569/2020/P1/Q8{]} }

S-Cut offers haircut service at a price based on age group at 60 outlets
located around Singapore. S-Cut has engaged you to develop an application
that runs on kiosk stationed at their outlets. The application uses
a relational database to store the data. Customers need to register
as a regular member with their name, contact number and price. They
can purchase a haircut service using the kiosks provided. The service
record should contain date of service, member information and the
outlet information. Based on the requirements given above, design
the database that consists of 3 tables: Member, Outlet and ServiceRecord.
\begin{enumerate}
\item {}
\begin{enumerate}
\item Draw the Entity-Relationship (E-R) diagram to show the tables in third
normal form (3NF) and their relationships between them. \hfill{}{[}3{]}
\item A table description can be expressed as:

\texttt{TableName( }\texttt{\uline{Attribute1}}\texttt{, Attribute2{*},
Attribute3, \dots ) }

The primary key is indicated by underlining one or more attributes.
Foreign keys are indicated by using a dashed underline/asterisk. Using
the information given, write table descriptions for the tables you
have identified in part \textbf{(a)(i)}. \hfill{}{[}5{]}
\end{enumerate}
\item To attract more customers, some outlets offer 20\% discount on Saturday
and Sunday. Write the table description with the changes to the database
to capture the change in price per haircut on Saturday and Sunday.
\hfill{}{[}1{]}
\item S-Cut offers platinum membership which entice members to additional
benefits. Platinum member needs to credit \$100 to their account which
entitles them to 12 sessions of haircut services, in addition they
will receive a birthday gift on their birthday month. To ensure greater
productivity in development of the membership system, object oriented
design is used. 
\begin{enumerate}
\item Draw a class diagram for member class(es) which exhibit the following: 
\begin{itemize}
\item Suitable classes with appropriate properties and methods
\item Inheritance 
\item Polymorphism \hfill{}{[}6{]}
\end{itemize}
\item Explain the term \textbf{encapsulation} and how it is applied in your
design in (c)(i). \hfill{}{[}2{]}
\item Explain the term \textbf{polymorphism} and how it is applied in your
design in (c)(i). \hfill{}{[}2{]}
\end{enumerate}
\item An alternative way to develop an application that runs on the kiosk
would be a web-based application. State \textbf{two} differences between
a native application and a web-based application. \hfill{}{[}2{]}
\item S-Cut collects data from the customer, describe \textbf{two} data
protection obligations on how S-Cut must comply with the Personal
Data Protection Act (PDPA). \hfill{}{[}2{]}
\end{enumerate}