\item \textbf{{[}NYJC/PRELIM/9569/2020/P1/Q6{]} }

Computers connected to the Internet use the TCP/IP suite of protocols
for data transmission.
\begin{enumerate}
\item What is a protocol? {[}1{]}
\item The TCP/IP stack is divided into four layers. One of these is the
application layer protocol. \textbf{Table 1} shows four different
scenarios that all use the TCP/IP protocol. Complete \textbf{Table
1} by writing the name of the particular \textbf{application layer
protocol} that would be used to transfer data during each operation.
You must give a different answer in each case.
\noindent \begin{center}
\textbf{Table 2}
\par\end{center}

\noindent \begin{center}
\begin{tabular}{|c|l|c|}
\hline 
 & \textbf{Operation} & \textbf{Application Layer Protocol }\tabularnewline
\hline 
\hline 
\textbf{(i)} & Managing a server remotely  & \tabularnewline
\hline 
\textbf{(ii)} & Retrieving e-mail from an e-mail server & \tabularnewline
\hline 
\textbf{(iii)} & Viewing a sports news web page using a web browser  & \tabularnewline
\hline 
\textbf{(iv)} & Accessing your online bank account using a web browser & \tabularnewline
\hline 
\end{tabular}
\par\end{center}

{[}4{]}
\item A student uses the following URL to download a copy of a previous
year\textquoteright s Computing exam paper.

$\mathtt{\underset{A}{\underbrace{https}}://\underset{B}{\underbrace{www.nanyang.moe.sg}}\underset{C}{\underbrace{/gce/computing/2019H2Computing2.pdf}}}$
\begin{enumerate}
\item Describe the \textbf{three} labelled parts (\texttt{A}, \texttt{B}
and \texttt{C}) of this URL.. \hfill{} {[}3{]}
\item State the top-level domain part in the URL. \hfill{} {[}1{]}
\end{enumerate}
\item To access the exam paper, the student\textquoteright s computer might
need to make use of a Domain Name System (DNS) query which is transmitted
to a DNS server.
\begin{enumerate}
\item What is the role of a DNS server? . \hfill{}{[}2{]}
\item In some circumstances the student\textquoteright s computer will not
need to contact a remote DNS server to access a resource. Describe
\texttt{two} situations when a DNS query will \texttt{not} be sent
to a remote DNS server. . \hfill{}{[}2{]}
\end{enumerate}
\item In the process of requesting a web page, a browser will generate an
HTTP GET request.
\begin{enumerate}
\item In which layer of the TCP/IP stack is the browser operating? . \hfill{}{[}1{]}
\item Explain why the student\textquoteright s computer might need to make
several HTTP GET requests to display one web page. . \hfill{}{[}2{]}
\item The HTTP GET requests are being sent to port 80 on the remote machine.
The browser has been allocated a \textbf{client port number}. What
is meant by a client port number?. \hfill{} {[}1{]}
\end{enumerate}
\end{enumerate}