\item \textbf{{[}NYJC/PRELIM/9569/2020/P1/Q7{]} }

Below is a numbered list of the names of some of the legislation that
applies in situations where computers are used:

1. Copyright, Designs and Patents Act 

2. Computer Misuse Act 

3. Regulation of Investigatory Powers Act 

4. Health and Safety Regulations 5. Data Protection Act

For each of the situations given below, identify the relevant legislation
which is being followed. Write the number that corresponds to the
appropriate legislation in each situation.
\begin{enumerate}
\item {}
\begin{enumerate}
\item Marcus wanted an MP3 of a recent song so he went to an online music
store. After paying he was able to immediately download the purchased
song. \hfill{}{[}1{]}
\item A new workstation is installed in an office and an assessment is performed
regarding the lighting for the workstation and the positioning of
the desk, monitor and chair. \hfill{}{[}1{]}
\item Mr Smith hands over his 50-character encryption key in response to
a request from the authorities investigating a fraud case. \hfill{}{[}1{]}
\end{enumerate}
\item The operators of a number of multi-storey car parks have installed
systems to scan and recognise number plates. The system is used at
both the entrance and exit of the car parks so that the arrival and
leaving times can be recorded.

Customers can set up an account so that money is automatically debited
when their car number plate is recognised as the car leaves the car
park. Customers who do not have an account can use their mobile phones
to pay the car parking fees by sending a text message to a specified
number with their number plate details and length of stay.

As these car parks are based around Singapore, the company also collects
location specific data. 
\begin{enumerate}
\item The company will need to follow the Data Protection Act as they will
be storing personal data. What is meant by personal data? \hfill{}{[}1{]}
\item Why might the storing of number plate details, mobile phone numbers
and location specific data be a concern for privacy campaigners? \hfill{}
{[}2{]}
\end{enumerate}
\item Explain with specific examples why a code of conduct for computing
professionals is necessary. \hfill{} {[}3{]}
\end{enumerate}