\item \textbf{{[}DHS/PRELIM/9569/2020/P2/Q3{]} }

A school needs a web application for teachers to use during English
lessons to record and view students' marks for weekly in-class presentations. 

The teacher should be required to login and should only be able to
input and view any information for students of the classes they teach. 

The maximum score per presentation is 100. Each English lesson is
always taught by the same teacher, each English lesson would only
have one teacher, and each class would only have one English lesson
per day. 

In a training session conducted for teachers, a demo version of the
app would be prepopulated with demo data as shown in the following
table. 
\noindent \begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
\textbf{Teacher's username } & \textbf{Teacher's password } & \textbf{Index number of student } & \textbf{Student's class } & \textbf{Date of presentation } & \textbf{Marks obtained}\tabularnewline
\hline 
\hline 
\texttt{mr\_raj } & \texttt{cr53aYJP } & \texttt{3 } & \texttt{19S306 } & \texttt{20200315 } & \texttt{95}\tabularnewline
\hline 
\texttt{mr\_james } & \texttt{8orjqiZc } & \texttt{24 } & \texttt{19S301 } & \texttt{20200315 } & \texttt{60}\tabularnewline
\hline 
\texttt{mdm\_rahayu } & \texttt{7iqndCjW} & \texttt{2 } & \texttt{19S302 } & \texttt{20200315 } & \texttt{35.5}\tabularnewline
\hline 
\texttt{mr\_james } & \texttt{8orjqiZc } & \texttt{11 } & \texttt{19S304 } & \texttt{20200325} & \texttt{60}\tabularnewline
\hline 
\end{tabular}
\par\end{center}

You have been tasked to create this web application. The data file
\texttt{DEMOAPP.txt} contains the demo data. 

\subsection*{Task 3.1 }

Create the user interface using HTML and CSS for the application.
The fields should include: 
\begin{itemize}
\item TeacherUsername 
\item TeacherPassword 
\item StudentIndex 
\item Class 
\item PresentationDate 
\item Marks The information should be presented in a tabular form. \hfill{}{[}7{]}
\end{itemize}

\subsection*{Task 3.2 }

Create a normalised relational database scheme for this application.
Provide the SQL statements for the creation of the tables. \hfill{}{[}6{]}

\subsection*{Task 3.3 }

Populate the table(s) with the demo data described above. Provide
SQL statements for the insertion of the records in \texttt{task3.sql}.\hfill{}
{[}4{]}

\subsection*{Task 3.4 }

Provide the processing logic in \texttt{app.py} and the associated
template file(s). \textcolor{white}{.}\hfill{}{[}13{]}

\subsection*{Task 3.5 }

Using SQL or otherwise, determine and display the total marks scored
by each class to the appropriate template file. \textcolor{white}{.}\hfill{}{[}5{]}