\item \textbf{{[}ACJC/PRELIM/9569/2021/P1/Q5{]} }

A printing shop offers printing services to its customers. When a
printing order is sent to the shop, the following information is recorded
down:
\begin{itemize}
\item Date of order 
\item Name of customer 
\item Number of copies 
\item Colour, or black and white, printing 
\item Whether express printing is required
\end{itemize}
The printing shop accepts three types of orders, leaflets, books and
posters.

Customers printing leaflets or books need to indicate if they require
single side or double side printing.

In addition, for books, the type of cover (hard cover or soft cover)
would need to be recorded. 

Leaflets and books are available in three sizes (A3, A4 or A5), while
posters are only available in a fixed size of A2.

For poster printing, customers have a choice of either glossy or matte
finishing.

The total charge to user is determined by the specifications of the
order and the formula is unique for each type of order.

This system is to be implemented using object-oriented programming
(OOP).
\begin{enumerate}
\item Draw a class diagram, showing:
\begin{itemize}
\item Any derived classes and inheritance from the base class 
\item The properties needed in the base, and any derived classes 
\item Suitable methods to support the system with at least one getter and
setter
\end{itemize}
The base class is \texttt{BASIC\_ORDER}. \hfill{}{[}8{]}
\item Explain the purpose of inheritance in object-oriented programing.
\hfill{}{[}2{]}
\end{enumerate}