\item \textbf{{[}DHS/PRELIM/9569/2020/P2/Q4{]} }

A dental clinic wishes to manage its patients' information using a
NoSQL database. 

There are 2 rooms in the clinic: Room 1 and Room 2. 

There are 3 dentists in the clinic: Doctor 1, Doctor 2, Doctor 3. 

Information about the patients is stored in the data file PATIENTS.txt
in the following format: 

\texttt{PatientID,Name,Appointment Date,Appointment Start Time,Doctor
Assigned,Room Number,Amount Charged }
\begin{itemize}
\item \texttt{PatientID} is an integer 
\item \texttt{Name} is made up of letters and space only 
\item \texttt{Appointment Date} is in DDMMYYYY format 
\item \texttt{Appointment Start} Time is HHMM in 24-hour format 
\item \texttt{Doctor Assigned} is either Doctor 1, Doctor 2 or Doctor 3 
\item \texttt{Room Number} is either Room 1 or Room 2 
\item \texttt{Amount Charged} is a float to 2 decimal places 
\end{itemize}

\subsection*{Task 4.1 }

Write program code to convert and import the data from \texttt{PATIENTS.txt}
into a MongoDB database Clinic under the collection \texttt{Patient}.
\hfill{}{[}4{]}

\subsection*{Task 4.2 }

Write program code to allow the Admin Clerk to add new patients by
requesting for the following information: 
\begin{itemize}
\item New patient's Name 
\item Appointment Date in DDMMYYYY format 
\item Appointment Start Time in 24-hour HHMM format 
\item Doctor to be Assigned 
\end{itemize}
The program should automatically assign a \texttt{PatientID}. Your
program should perform the necessary validation for each field. \hfill{}{[}8{]}

\subsection*{Task 4.3}

The Admin Clerk wants to know if there are issues with appointments.
Write program code to output appointments clashes and double bookings.
If an appointment clash occurs, reschedule the latter appointment
to the nearest available appointment on the same date. If a double
booking occurs, delete the latter duplicate booking. \hfill{}{[}8{]}

\subsection*{Task 4.4 }

Write program code for the Admin Clerk to determine the top 3 paying
patients. \hfill{} {[}4{]}

\subsection*{Task 4.5 }

The Admin Clerk realised that there are patients with the same name.
Write program code to identify patients with the same names and output
their \texttt{PatientID}s. \hfill{} {[}3{]}