\item \textbf{{[}JPJC/PRELIM/9569/2020/P1/Q2{]} }

Every sales transaction made in JPJC supermarket is stored as a record
in a serial file for auditing purposes. At the end of each day, a
copy of the daily serial file, sorted by transaction amount in descending
order will be archived into the main database. 
\begin{enumerate}
\item State what is meant by a serial file? \hfill{}{[}1{]}
\item Explain how an archive file is different from a backup file, and describe
how a backup file for sales transactions can be created for JPJC supermarket.\hfill{}
{[}2{]}
\end{enumerate}
Merge sort algorithm is used to arrange the sales transaction records
by ordering them in descending order of transaction amounts. The algorithm
will first read all the daily unsorted sales transactions into \texttt{A},
a fixed size array of records with index starting from 1. Then, \texttt{mergesort}
will be applied to sort \texttt{A}. The pseudocode for \texttt{mergesort}
is given below, 

\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{PROCEDURE mergesort(A: ARRAY of RECORDS, x, y: INTEGERS)}

\texttt{\qquad{}IF x < y }

\texttt{\qquad{}\qquad{}THEN }

\texttt{\qquad{}\qquad{}\qquad{}m x + ((y - x) DIV 2) //DIV performs
integer division }

\texttt{\qquad{}\qquad{}\qquad{}mergesort(A, x, m) }

\texttt{\qquad{}\qquad{}\qquad{}mergesort(A, m + 1, y) }

\texttt{\qquad{}\qquad{}\qquad{}merge(A, x, m, y) }

\texttt{\qquad{}ENDIF }

\texttt{ENDPROCEDURE }

\texttt{//-{}-{}-main program-{}-{}- }

\texttt{mergesort(A, x, y) }%
\end{minipage}

Given that array \texttt{A = {[}39.10, 17.50, 35.40, 42.68, 8.90,
35.40{]}}, and \texttt{merge(A, x, m, y)} will sort and combine elements
of \texttt{A{[}x:m{]}}, and \texttt{A{[}m+1:y{]}} into \texttt{A{[}x:y{]}}
in descending order. 
\begin{enumerate}
\item[(c)]  State the values of \texttt{x}, and \texttt{y} when \texttt{mergesort}
is called in the main program.\hfill{} {[}2{]}
\item[(d)]  State the total number of times \texttt{mergesort} and \texttt{merge}
are called in the entire program.\hfill{} {[}2{]}
\end{enumerate}
The following diagram shows an incomplete trace tree diagram of the
array of sales transaction records represented by its sales amount. 
\begin{enumerate}
\item[(e)]  Draw and complete the trace tree diagram above by applying merge
sort to the unsorted array of records A. \hfill{}{[}4{]}
\item[(f)]  The time complexity for merge sort is $O(N\log_{2}N)$. Explain
why this time complexity is applicable to the best, average and worst
case scenarios.\hfill{} {[}1{]}
\end{enumerate}