\item \textbf{{[}YIJC/PRELIM/9569/2020/P1/Q4{]} }

\emph{HoLi Tea} is a popular chain selling a wide variety of bubble
tea. Each drink is categorised by the flavor (e.g. brown sugar, peppermint,
lemon \dots ), the type of tea leaves used (e.g. green tea, red tea,
black tea \dots ), the pearl options (e.g. black pearl, white pearl,
or no pearl) and the price. 

There are two variants of bubble tea: Milk Tea and Fruit Tea. Each
milk tea has a specific type of milk used (e.g. fresh milk, condensed
milk) and some milk tea come with pudding. Some fruit tea include
cultured milk. 

The owner of HoLi Tea intends to use object-oriented programming language
to store and process the information on the types of drink in the
self-ordering web application system. 

The base class \texttt{BUBBLE\_TEA} has a method to display the properties
of the bubble tea. 
\begin{enumerate}
\item {}
\begin{enumerate}
\item Draw a UML class diagram showing:\hfill{}{[}6{]}
\begin{itemize}
\item any derived classes and inheritance from the base class 
\item the properties needed in the base, and any derived classes 
\item suitable methods to support the system with at least one getter and
one setter method
\end{itemize}
\item Explain why inheritance is an important feature of object-oriented
programming.\hfill{} {[}2{]}
\item Explain why polymorphism is useful in object-oriented programming.
\hfill{}{[}2{]}
\end{enumerate}
\emph{HoLi Tea} has a loyalty programme to reward their regular customers.
Members are entitled to a 20\% discount for their purchases and a
free drink on their birthday. To pay tribute to the frontline workers
during the COVID-19 pandemic, all frontline workers are entitled to
a 20\% discount for their purchases, and those who are also members
will receive a free drink on any day. 
\item {}
\begin{enumerate}
\item Create a decision table showing all the possible conditions and actions.
\hfill{}{[}5{]}
\item Simplify your decision table by removing redundancies. \hfill{}{[}3{]}
\end{enumerate}
\end{enumerate}