\item \textbf{{[}ALVL/9569/2020/P1/Q1{]} }

A software company is writing a program for a vehicle hire business.
Both cars and vans are available for hire. 

For all vehicles, the data that will be stored include: 

\begin{singlespace}
~~~~Vehicle Registration Number (VRN) 

~~~~Model 

~~~~Total distance travelled (km) 

~~~~Date hired 

~~~~Date of return 

~~~~Cost per day 

~~~~Available for hire 
\end{singlespace}

For cars. the additional data stored include: 

\begin{singlespace}
~~~~Number of seats 

~~~~Fuel type (petrol, diesel. electric. hybrid) 
\end{singlespace}

For vans. the additional data stored include: 

\begin{singlespace}
~~~~Load volume ($\text{m}^{3}$) 

~~~~Maximum load (kg) 
\end{singlespace}

The odometer in the vehicle displays the total distance the vehicle
has travelled since manufacture. 

When a vehicle is hired: 
\begin{itemize}
\begin{singlespace}
\item total distance travelled is set to the odometer's value
\item date hired is set to the current date
\item return date is set to the date the vehicle is expected to be returned 
\item available for hire is set to \texttt{FALSE}. 
\end{singlespace}
\end{itemize}
When a vehicle is returned: 
\begin{itemize}
\begin{singlespace}
\item hire cost is returned as the cost per day multiplied by the number
of days the vehicle was hired 
\item total distance travelled is set to the odometer value 
\item date returned is set to the current date 
\item available for hire is set to \texttt{TRUE}.
\end{singlespace}
\end{itemize}
Object-oriented programming will be used to model vehicles. 
\begin{enumerate}
\item Draw a class diagram that shows the following for the situation described
above. 
\begin{itemize}
\begin{singlespace}
\item the superclass
\item any subclasses
\item inheritance 
\item properties 
\item appropriate methods \hfill{} {[}12{]}
\end{singlespace}
\end{itemize}
\item State the purpose of a superciass. Give an example of a superciass
from the vehicle hire example. \hfill{} {[}2{]}
\end{enumerate}
Objects provide encapsulation of properties and methods.
\begin{enumerate}
\item[\textbf{(c)}] State the purposes of encapsulation. \hfill{} {[}2{]}
\end{enumerate}
The business wants to change the way the hire cost is calculated for
a car. As well as charging per day, an additional charge of \$0.05
is to be made per km travelled during this hire.
\begin{enumerate}
\item[\textbf{(d)}] Suggest a change to the class diagram to enable the new charging
scheme to be used for cars. \hfill{} {[}1{]}
\item[\textbf{(e)}] State the purpose of polymorphism. \hfill{} {[}1{]}
\end{enumerate}