\item \textbf{{[}ACJC/PRELIM/9569/2021/P1/Q4{]} }

Merge sort and bubble sort are two sorting algorithms that can be
applied to sort a list of integers in ascending order.
\begin{enumerate}
\item By briefly comparing the operation of merge sort and bubble sort,
state which algorithm would be more efficient. \hfill{}{[}3{]}
\end{enumerate}
The pseudocode for the recursive \texttt{MergeSortDesc} function is
shown below, which takes in a list of integers and returns a new list
with the integers sorted in descending order. It makes use of the
\texttt{MergeDesc} function in line \texttt{10} that merges two lists
of integers sorted in descending order into a single list of integers
sorted in descending order as well.

\fbox{\begin{minipage}[t]{0.8\columnwidth}%
\texttt{01 FUNCTION MergeSortDesc(MyList: LIST) RETURNS LIST }

\texttt{02 \qquad{}MaxIndex \textleftarrow{} LENGTH(MyList) }

\texttt{03 \qquad{}\qquad{}IF ......A...... }

\texttt{04 \qquad{}\qquad{}\qquad{}THEN }

\texttt{05 \qquad{}\qquad{}\qquad{}Half \textleftarrow{} ......B...... }

\texttt{06 \qquad{}\qquad{}\qquad{}LeftList \textleftarrow{} LEFT(MyList,
Half) }

\texttt{07 \qquad{}\qquad{}\qquad{}RightList \textleftarrow{} RIGHT(MyList,
Half) }

\texttt{08 \qquad{}\qquad{}\qquad{}SortedLeftList \textleftarrow{}
MergeSortDesc(LeftList) }

\texttt{09 \qquad{}\qquad{}\qquad{}SortedRightList \textleftarrow{}
MergeSortDesc(RightList) }

\texttt{10 \qquad{}\qquad{}\qquad{}Result \textleftarrow{} MergeDesc(SortedLeftList,
SortedRightList) }

\texttt{11 \qquad{}\qquad{}ELSE }

\texttt{12 \qquad{}\qquad{}\qquad{}......C...... }

\texttt{13 \qquad{}\qquad{}ENDIF }

\texttt{14 \qquad{}\qquad{}RETURN Result }

\texttt{15 ENDFUNCTION}%
\end{minipage}}
\begin{enumerate}
\item[(b)] State what is meant by a \textbf{recursive} function. \hfill{}{[}2{]}
\item[(c)] Write the pseudocode for \texttt{A}, \texttt{B} and \texttt{C} in
the algorithm. \hfill{}{[}3{]}
\item[(d)] Describe the operation of the \texttt{MergeDesc} function.

Assume that the function does not modify the two input lists.\hfill{}
{[}4{]}
\end{enumerate}