\item \textbf{{[}HCI/PRELIM/9569/2021/P1/Q1{]} }

An E-Commerce company stores the following data of customers in the
system. 
\begin{itemize}
\item Name 
\item Contact 
\item Address 
\end{itemize}
It categories its customers into 2 types of loyalty programs. 
\begin{itemize}
\item Spend-based loyalty program 
\item Paid loyalty program 
\end{itemize}
Customers of Spend-based loyalty program earn one point for every
block of \$10 spent in a single order, whereas customers of Paid loyalty
program pay a monthly or annual fee. Customers of Paid loyalty program
will enjoy the benefits of having early access to sales events and
free delivery for purchases above \$30. 

For Spend-based loyalty program, the additional data stored include: 
\begin{itemize}
\item Points earned 
\end{itemize}
For Paid loyalty program, the additional data stored include: 
\begin{itemize}
\item Payment schedule (monthly or annually) and corresponding fee 
\item Next payment date, computed based on payment schedule and the date
of enrollment to the program 
\end{itemize}
Object-oriented programming will be used to model the customers. 
\begin{enumerate}
\item Draw a class diagram that shows the following for the requirement
described above.
\begin{itemize}
\item the superclass 
\item any subclasses 
\item inheritance 
\item properties 
\item appropriate methods \hfill{}{[}6{]}
\end{itemize}
\end{enumerate}
The company makes changes to the Paid loyalty program to allow the
customer in the program to earn ten points for every block of \$20
spent in a single order, in addition to the current benefits. The
points earned do not expire. For Spend- based loyalty program, all
points earned will expire on the anniversary of the date of enrolment
to the program. 
\begin{enumerate}
\item[(b)]  Suggest changes required to the class diagram to enable the changes.\hfill{}
{[}3{]}
\item[(c)]  Explain why inheritance is an important feature of object-oriented
programming.\hfill{} {[}1{]}
\end{enumerate}
To attract customers to enrol to its Paid loyalty program, the company
launches an invitation campaign to invite Spend-based loyalty program
customers who qualified the following conditions: 
\begin{itemize}
\item Customer who earned more than 2000 points in a year and has an average
of at least one order per month will be contacted by staff. 
\item Customer who has enrolled for at least a year and has an average of
at least one order per month will be sent an invitation email. 
\item Otherwise, no invitation will be sent. 
\end{itemize}
\begin{enumerate}
\item[(d)]  Create a decision table showing all the possible outcomes and results.
\hfill{}{[}4{]}
\item[(e)]  Simplify your decision table by removing redundancies.\hfill{}
{[}2{]}
\end{enumerate}