\item \textbf{{[}RVHS/PRELIM/9569/2021/P1/Q6{]} }

Study the following sorting code carefully. 

\noindent %
\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{def sort(lst): }

\texttt{\qquad{}if len(lst)<=1: }

\texttt{\qquad{}\qquad{}return lst }

\texttt{\qquad{}else: }

\texttt{\qquad{}\qquad{}pivot = lst{[}0{]} }

\texttt{\qquad{}\qquad{}smaller = {[}{]} }

\texttt{\qquad{}\qquad{}larger = {[}{]} }

\texttt{\qquad{}\qquad{}for i in range (1, len(lst)): }

\texttt{\qquad{}\qquad{}\qquad{}if lst{[}i{]} < pivot: }

\texttt{\qquad{}\qquad{}\qquad{}\qquad{}smaller.append(lst{[}i{]}) }

\texttt{\qquad{}\qquad{}\qquad{}else: }

\texttt{\qquad{}\qquad{}\qquad{}\qquad{}larger.append(lst{[}i{]}) }

\texttt{\qquad{}\qquad{}return sort (smaller) + {[}pivot,{]} + sort
(larger) }%
\end{minipage}
\begin{enumerate}
\item State the name of the above sorting algorithm. \hfill{}{[}1{]}
\item Explain why the above sorting algorithm is inefficient when it is
used on a nearly sorted array. \hfill{} {[}1{]}
\item Explain how you can modify the code to improve the efficiency. \hfill{}{[}2{]}
\end{enumerate}
Bubble sort and insertion sort are both used to sort a nearly sorted
integer array of size 1000 and there are only 5 integers in the array
that are not in the correct position. 
\begin{enumerate}
\item State and explain why insertion sort generally perform better than
bubble sort for nearly sorted array. \hfill{}{[}2{]}
\item Draw a flow chart for the algorithm described below. \hfill{}{[}4{]}

Given an integer \texttt{k} and an array \texttt{arr{[}{]}} representing
the destination floors for \texttt{n} people waiting currently at
the ground floor and \texttt{k} is the capacity of the elevator. It
takes 1 unit time for the elevator to reach any consecutive floor
from the current floor. The algorithm finds the minimal time taken
to get all the people to their destination floor and then return to
the ground floor. 

\noindent\begin{minipage}[t]{1\columnwidth}%
\texttt{def minTime(n, k, arr) : }

\texttt{\qquad{}\# Sort in descending order }

\texttt{\qquad{}arr.sort(reverse = True) }

\texttt{\qquad{}minTime = 0 }

\texttt{\qquad{}\# Iterate through the groups }

\texttt{\qquad{}for i in range(0, n, k) : }

\texttt{\qquad{}\qquad{}\# Update the time taken for }

\texttt{\qquad{}\qquad{}\# each group }

\texttt{\qquad{}\qquad{}minTime += (2 {*} arr{[}i{]}) }

\texttt{\qquad{}\# Return the total time taken }

\texttt{\qquad{}return minTime}%
\end{minipage} 
\end{enumerate}