\item \textbf{{[}YIJC/PRELIM/9569/2021/P2/Q1{]} }

During a contact tracing exercise, the TraceTogether token\textquoteright s
tag number, the user\textquoteright s name and the user\textquoteright s
mobile number are stored in an Abstract Data Type (ADT) \texttt{Person}.
The information are stored as a three element tuple as follows: 
\noindent \begin{center}
\texttt{(tag: INTEGER, name: STRING, hp: STRING) }
\par\end{center}

\noindent \begin{center}
\begin{tabular}{|c|c|c|}
\hline 
\textbf{Function } & \textbf{Return Type } & \textbf{Description}\tabularnewline
\hline 
\texttt{make\_person(tag,name,hp) } & \texttt{Person ADT } & A Constructor to create the \texttt{Person} ADT.\tabularnewline
\hline 
\texttt{get\_tag(Person) } & \texttt{INTEGER } & Returns the tag number of the user. \tabularnewline
\hline 
\texttt{get\_name(Person) } & \texttt{STRING } & Returns the name of the user.\tabularnewline
\hline 
\texttt{get\_hp(Person) } & \texttt{STRING } & Returns the mobile number of the user.\tabularnewline
\hline 
\end{tabular}
\par\end{center}

\subsubsection*{Task 1.1 }

Write program code to implement the ADT \texttt{Person} with the above
constructor and accessors.\hfill{} {[}4{]}

\subsubsection*{Task 1.2 }

Write program code for the function \texttt{read\_file()} to read
all the 21 users\textquoteright{} information from the file \texttt{PEOPLE.csv}
and return a list containing all the \texttt{Person} ADTs.\hfill{}
{[}5{]}

\subsubsection*{Task 1.3 }

Write program code for the function \texttt{insertion\_sort(lst)}
that takes the list \texttt{lst} obtained from \textbf{Task 1.2} and
sort them according to their tag numbers in an ascending order using
the insertion sort algorithm.\hfill{} {[}5{]}

Searching for a tag number in a large list of users may be slow and
tedious. However, if the list is sorted, performing a binary search
would be more efficient. 

\subsubsection*{Task 1.4 }

Write program code for the function \texttt{search(lst,num)} that
searches for a tag number \texttt{num} in the sorted list \texttt{lst}
obtained from \textbf{Task 1.3}. The code should 
\begin{itemize}
\item perform a binary search on the sorted list. 
\item return the \texttt{Person} ADT if the tag number \texttt{num} exists.
Otherwise, return \texttt{None}. 
\item print the number of comparisons made in the searching process.\hfill{}
{[}8{]}
\end{itemize}