\item \textbf{{[}ACJC/PRELIM/9569/2021/P1/Q1{]} }

A famous restaurant only accommodates one seating daily from 6.00
pm to 8.00 pm. It has 10 tables, each with a maximum capacity between
2 and 8 people. Advanced reservation is required to dine in at the
restaurant. 

The owner of the restaurant decides to write a program to handle reservations.
As a trial, it can only take a booking for one evening only. 

A procedure to initialise the arrays \texttt{MaxSize}, \texttt{IsBooked}
and \texttt{GroupSize} has been defined. The indexes of each array
corresponds to the table number.

\begin{tabular}{|c|c|}
\multicolumn{1}{c}{Index} & \multicolumn{1}{c}{\texttt{MaxSize}}\tabularnewline
\hline 
1 & 2\tabularnewline
\hline 
2 & 2\tabularnewline
\hline 
3 & 4\tabularnewline
\hline 
4 & 4\tabularnewline
\hline 
5 & 4\tabularnewline
\hline 
6 & 6\tabularnewline
\hline 
7 & 6\tabularnewline
\hline 
8 & 6\tabularnewline
\hline 
9 & 8\tabularnewline
\hline 
10 & 8\tabularnewline
\hline 
\end{tabular}%
\begin{tabular}{|c|c|}
\multicolumn{1}{c}{} & \multicolumn{1}{c}{\texttt{IsBooked}}\tabularnewline
\hline 
1 & FALSE\tabularnewline
\hline 
2 & FALSE\tabularnewline
\hline 
3 & FALSE\tabularnewline
\hline 
4 & FALSE\tabularnewline
\hline 
5 & FALSE\tabularnewline
\hline 
6 & FALSE\tabularnewline
\hline 
7 & FALSE\tabularnewline
\hline 
8 & FALSE\tabularnewline
\hline 
9 & FALSE\tabularnewline
\hline 
10 & FALSE\tabularnewline
\hline 
\end{tabular}%
\begin{tabular}{|c|c|}
\multicolumn{1}{c}{} & \multicolumn{1}{c}{\texttt{GroupSize}}\tabularnewline
\hline 
1 & \tabularnewline
\hline 
2 & \tabularnewline
\hline 
3 & \tabularnewline
\hline 
4 & \tabularnewline
\hline 
5 & \tabularnewline
\hline 
6 & \tabularnewline
\hline 
7 & \tabularnewline
\hline 
8 & \tabularnewline
\hline 
9 & \tabularnewline
\hline 
10 & \tabularnewline
\hline 
\end{tabular}

The procedure \texttt{BookTable} is shown below. When a booking enquiry
is made, the number of customers is keyed in. 

\fbox{\begin{minipage}[t]{0.8\columnwidth}%
\texttt{01 PROCEDURE BookTable }

\texttt{02 \qquad{}DECLARE NumberOfCustomers, TableNumber : INTEGERS }

\texttt{03 \qquad{}DECLARE Found : BOOLEAN}

\texttt{04 \qquad{}INPUT NumberOfCustomers }

\texttt{05 \qquad{}TableNumber \textleftarrow{} 0 }

\texttt{06 \qquad{}FOUND \textleftarrow{} False }

\texttt{07 \qquad{}REPEAT }

\texttt{08 \qquad{}\qquad{}TableNumber \textleftarrow{} TableNumber
+ 1 }

\texttt{09 \qquad{}\qquad{}IF MaxSize{[}TableNumber{]} > NumberOfCustomers
AND IsBooked{[}TableNumber{]} = FALSE }

\texttt{10 \qquad{}\qquad{}\qquad{}THEN }

\texttt{11 \qquad{}\qquad{}\qquad{}\qquad{}Found \textleftarrow{}
TRUE }

\texttt{12 \qquad{}\qquad{}ENDIF }

\texttt{13 \qquad{}UNTIL Found = TRUE AND TableNumber = 10 }

\texttt{14 \qquad{}\qquad{}IF Found = FALSE }

\texttt{15 \qquad{}\qquad{}\qquad{}THEN }

\texttt{16 \qquad{}\qquad{}\qquad{}OUTPUT \textquotedbl No tables
with enough seats available.\textquotedbl{} }

\texttt{17 \qquad{}\qquad{}\qquad{}ELSE }

\texttt{18 \qquad{}\qquad{}\qquad{}\qquad{}GroupSize{[}TableNumber{]}
\textleftarrow{} NumberOfCustomers }

\texttt{19 \qquad{}\qquad{}\qquad{}\qquad{}OUTPUT \textquotedbl Booking
is successful! Table no:\textquotedbl , TableNumber }

\texttt{20 \qquad{}ENDIF }

\texttt{21 ENDPROCEDURE}%
\end{minipage}}
\begin{enumerate}
\item There are two errors and one missing line of code in the procedure
above.
\begin{enumerate}
\item Name the type of the errors. \hfill{}{[}1{]}
\item Describe the errors and the changes required to correct them. \hfill{}{[}3{]}
\item Write the missing line of code and state where it should be located.
\hfill{}{[}2{]}
\end{enumerate}
\item Once the procedure \texttt{BookTable} is able to run correctly, the
owner decides to improve its functionality.

The procedure should ask the user to input the name and the mobile
number of the person making the reservation when a table with enough
seats can be found.

Name and describe two data validation techniques that can be applied
to any of the inputs mentioned above.\hfill{} {[}2{]}
\item Explain the difference in the type of memory allocation for an array
and a linked list. \hfill{}{[}2{]}
\end{enumerate}